### 2017-11-14 LaTeX/MonthlyReports.tex
template for monthly reports

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts
%SetFonts

\title{N43DA-17-1216; HHSN271201700053C \\
Enhanced Research Network Information Environment (ERNIE)\\
Monthly Progress Reports}
\author{George Chacko, NETE}
\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{Monthly Reports}
\subsection*{Oct 15-Nov 15, 2017}

This second report covers accomplishments in the second month of the ERNIE project. The focus of our efforts was to develop working protocols, extend the infrastructure and begin work on the first four of seven case studies to be completed.

\begin{itemize}
\item Update processes were added to the Jenkins automation server to monitor refreshes
\item Backups, anti-virus, and OS snapshots have been setup for ERNIE data
\item De-duplication, primary keys, and other curation workflows have been set up.
\item A Solr server was created to index the contents for ERNIE for fast searching and is being tested to find citations for poorly defined references typically found in patent citations, e.g. "Johnson et al, 1989".
\item An XML specification (DTD) was designed to collect case study data for the two validation (ipilimumab and ivacaftor) and the two other drug case studies (buprenorphine and naltrexone). A script was generated to assemble a complete XML file in compliance with the DTD.
\item A SQL script was developed to be able to take either a list of pmids as input or a list of Web of Science ids (UT) and extract one or more generation of cited references and then map all publications to NIH awards.
\item Basic case study data was assembled for ipilimumab, ivacaftor, buprenorphine, and naltrexone. These data are expected to be enriched in November and December as we revise our collection scripts and add new data sources. These data are on our Github server.
\item Network analysis code is being developed to generate in network article scores and the PIR metric (Williams et al., 2015) for all case studies using ERNIE generated data.
\item Work has commenced on the Affymetrix Amplichip CYP450 kit and we have identified a number of potential data sources for the Life Skills Training case study. The DiscoverX case study will begin in December 2017.
\end{itemize}

\subsection*{Challenges} Whereas developing the infrastructure has been relatively routine, the case studies identified by NIDA, particularly the non-drug case studies have required extended discussion and experimentation within the group to be able to generate useful results. The Affymetrix Genechip is an example since it is really a composite of a hardware platform, advances in photolithography and synthetic chemistry that enable arrays to be developed on solid supports, software to analyze results, and expression profiling in various systems. In addition the kit from Roche, Amplichip represents a second manufacturer. Focusing on cytochromes in the area of NIDA's interests has also required different strategies from the `pinnacle event' approach of FDA approved therapeutics. In addition, Affymetrix has been recently acquired by Thermo-Fisher and information is distributed over a legacy website as well as an incompletely populated new website. These challenges were largely anticipated and are being negotiated systematically. We believe that many of these will be resolved in late November and December 2017. To manage these challenges we have switched to a parallelized approach to the case studies rather than process them serially. This enables refinement of the data in each case study even as we make advances.

\subsection*{Questions and Comments for Dr. Sazonova}

\begin{itemize}
 \item You had mentioned consulting with the Office of Science Policy as an option. Would it be possible to get any recommendations for policy sites we should consider, particularly for the Life Skills Training case study but also for others? We have a list that we would be happy to share that includes the recent recommendations to President Trump.
 \item You commented that NIDA had invested in developing the Affymetrix Genechip technology for cytochrome P450 profiling. Searches of NIH RePORTER does not have much information in this regard. Would it be possible to get a list of NIDA grants and contracts that you believe represent these investments in CYP450 expression profiling. We'd like to make sure that they are included in the case study.
 \item We received an invitation to apply for the I-Corps program.``Review FOA PA-18-314 and apply for the I-Corps at NIH April 2018 session'' This is of interest to us, the application is due in December. Are you able to offer any advice?
 \item We were contacted by Foresight Science \& Technology Inc., an OER contractor and they are conducting a niche assessment for our project at no charge
 \end {itemize}

\pagebreak
\subsection*{Oct 13, 2017}

This first monthly report covers accomplishments in the first month of the ERNIE project. Setting up infrastructure was the overarching goal for the first month.

\begin {itemize}
\item A development server, ernie1.eastus2.cloudapp.azure.com, was created as a virtual machine in the Microsoft Azure cloud. The server is set up with 8 Tb of storage and runs Linux Centos 7.3. Secure access is maintained through two factor authentication (2FA) to protect data and from unauthorized access.
\item PostgreSQL 9.6 was installed on the development server and configured to accommodate the ERNIE data model. The following data were loaded into the PostgreSQL database. Excluding staging data, and temporary tables the database presently contains over 3.09 billion records to date.

\begin {itemize}
\item The Web of Science Core Collection (updated weekly)
\item The Derwent Patent Citation Index  (updated weekly)
\item The National Clinical Trials Database  (updated weekly)
\item The FDA Orange and Purple Books  (updated monthly)
\item Clinical guidelines from the AHRQ National Clinical Guideline Clearinghouse (updated weekly)
\item NIH grants data from NIH ExPORTER (updated monthly)
\end {itemize}

\item A number of automation processes relying on Jenkins Continuous Integration technology have been put in place to handle updates to these data.
\item A JIRA site has been established for Agile project management. Dr. Sazonova has access to this site along with our two collaborators, Drs. Onken and Pico.
\item A Github site has been established for code management, archival, and dissemination.https://netesolutions.github.io/ERNIE/
\end {itemize}

\end{document}

### 2017-11-15 LaTeX/MonthlyReports.tex
minor updates before sending to PO

@@
 \item De-duplication, primary keys, and other curation workflows have been set up.
-\item A Solr server was created to index the contents for ERNIE for fast searching and is being tested to find citations for poorly defined references typically found in patent citations, e.g.
-"Johnson et al, 1989".
+\item A Solr server was created to index the contents for ERNIE for fast searching and is being tested to find citations for references typically found in patents.
 \item An XML specification (DTD) was designed to collect case study data for the two validation (ipilimumab and ivacaftor) and the two other drug case studies (buprenorphine and naltrexone).
@@
 \item Network analysis code is being developed to generate in network article scores and the PIR metric (Williams et al., 2015) for all case studies using ERNIE generated data.
-\item Work has commenced on the Affymetrix Amplichip CYP450 kit and we have identified a number of potential data sources for the Life Skills Training case study.
+\item Work has commenced on the Affymetrix platform for expression profiling of CYP450 genes and we have also identified a number of potential data sources for the Life Skills Training case study.
 The DiscoverX case study will begin in December 2017.
@@
 Focusing on cytochromes in the area of NIDA's interests has also required different strategies from the `pinnacle event' approach of FDA approved therapeutics.
-In addition, Affymetrix has been recently acquired by Thermo-Fisher and information is distributed over a legacy website as well as an incompletely populated new website.
-These challenges were largely anticipated and are being negotiated systematically.
-We believe that many of these will be resolved in late November and December 2017.
+These challenges were largely anticipated and are being negotiated systematically and we believe that many of these will be resolved in late November and December 2017.
+We also note that Affymetrix has been recently acquired by Thermo-Fisher and its information is now distributed over a legacy website as well as an incompletely populated new website.
 To manage these challenges we have switched to a parallelized approach to the case studies rather than process them serially.
 This enables refinement of the data in each case study even as we make advances.
+
+A second set of challenges represents finding the right balance between expert curation and automation, in other words managing scalability.
+The use of Apache Solr as a search technology is a step forward but some references such as, "Johnson et al.
+(1989)" can only be guessed at by a human being with some scientific training.
+In the end the use of a big data approach relies not having to resort to exhaustive collection so we believe that we will be able to provide valuable information with the approach we envisioned when writing our proposal.
 
@@
 \begin{itemize}
- \item You had mentioned consulting with the Office of Science Policy as an option.
+ \item During the kickoff meeting Dr Sazonova mentioned consulting with the Office of Science Policy.
 Would it be possible to get any recommendations for policy sites we should consider, particularly for the Life Skills Training case study but also for others?
-We have a list that we would be happy to share that includes the recent recommendations to President Trump.
- \item You commented that NIDA had invested in developing the Affymetrix Genechip technology for cytochrome P450 profiling.
+We have a list that we would be happy to share that includes the recent recommendations to President Trump on opioid addiction.
+ \item Dr.
+Sazonova commented that NIDA had invested in developing the Affymetrix Genechip technology for cytochrome P450 profiling.
 Searches of NIH RePORTER does not have much information in this regard.
@@
 Are you able to offer any advice?
- \item We were contacted by Foresight Science \& Technology Inc., an OER contractor and they are conducting a niche assessment for our project at no charge
+ \item We were contacted by Foresight Science \& Technology Inc., an OER contractor and they are conducting a market niche assessment for our project at no charge
  \end {itemize}

### 2017-12-01 Template_Job/template.sh
Enhancing template job

@@ -1,0 +1,14 @@
+#!/usr/bin/env bash
+cd `dirname $0`
+
+echo "Executing Postgres script..."
+# -a = --echo-all: pPrint all nonempty input lines to standard output as they are read.
+# -h localhost switches from Unix sockets to TCP/IP
+psql -a -v ON_ERROR_STOP=on -f template_query.sql -h localhost ernie ernie_admin
+
+echo "Executing Python script..."
+# Unquoted $SWITCHES get expanded into *multiple* command-line arguments
+# Quoted $SWITCHES get expanded into a *single* command-line argument
+python template.py -t test 'argument with spaces' $switches
+
+echo "Done."

### 2017-12-04 LaTeX/Paper2/paper2.tex

\documentclass[review]{elsarticle}

\usepackage{lineno,hyperref}
\modulolinenumbers[5]

\journal{Heliyon}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%
%George's Additions
%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{subcaption}
\usepackage{changepage}
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{amsmath,amssymb}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem{lemma}[theorem]{Lemma}

%% Misc. Packages
\usepackage[final]{changes}
\definechangesauthor[name={George Chacko}, color=orange]{gc}
\setremarkmarkup{(#2)}
\usepackage{listings}

\begin{document}

\begin{frontmatter}

\title{XX}
%\tnotetext[mytitlenote]{This document is a collaborative effort}

%% Group authors per affiliation:
%% or include affiliations in footnotes:
\author[nl]{Samet Keserci}

\author[nl]{Avon Davey}

\author[ca]{Di Cross}

\author[gi]{Alexander R. Pico}

\author[nl]{George Chacko \corref{cor1}}
\ead{netelabs@nete.com}

\cortext[cor1]{Corresponding author}
%\fntext[fn1]{Current address: Facebook Inc., Menlo Park, CA, USA}

\address[nl]{NETE Labs, NET ESolutions Corporation, McLean, VA, USA}
\address[cal]{XX, USA}
\address[gi]{Gladstone Institutes, San Francisco, CA, USA}

\raggedright
\begin{abstract}
\end{abstract}

%\begin{keyword}
%\end{keyword}

\end{frontmatter}

\linenumbers
\raggedright
\section{Introduction}

\section{Materials and Methods}

\section*{Results and Discussion} 
\section*{Acknowledgments} This study would not have been possible without data that is made publicly available by NIH and the FDA. We thank Tandy Warnow from the University of Illinois Urbana-Champaign for critical comments and advice on formalizing definitions. We also thank Sandeep Somaiya and Syd Gomes from NETE as well as Holly J. Falk-Krzesinski, Daniel Calto, M'hamed Aisati, and Sherif El Shamy from Elsevier for their support of this collaboration.

\section{References}

\begin{thebibliography}{10}
\raggedright

\bibitem{bibWilliams}
Williams RS, Lotia S, Holloway AK, Pico AR.
\newblock {{F}rom Scientific Discovery to Cures: Bright Stars within a Galaxy.}
\newblock Cell. 2015 163:21-23. doi: 10.1016/j.cell.2015.09.007

\end{thebibliography}

\begin{figure}[!h]
%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\scalebox{0.99}
{
\begin{subfigure}{.5\textwidth}
  \centering
%  \includegraphics[width=.95\linewidth]{}
  \label{fig:sub1}
\end{subfigure}
\begin{subfigure}{.5\textwidth}
  \centering
 % \includegraphics[width=.95\linewidth]{}
  \label{fig:sub2}
\end{subfigure}
}
\caption{{\bf Intersecting Publications in Five Networks} Intersections were calculated across all five networks for the first generation of references (citing\_pmids) and 
as well as for the second generation of references (cited\_sids) and displayed as Venn diagrams. \emph{Left Panel.} No first generation publications are observed common to all five networks. A single publication is cited in four of five networks. \emph{Right Panel.} 14  publications are common to all five networks. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib)}
\label{fig: test}
%\end{adjustwidth}
\end{figure}

\begin{figure}[!h]
%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
%\scalebox{1.3}{
%\includegraphics[scale=0.1]{cy_core14_v2csv_5b.png}}
\caption{{\bf Core Publications in Networks}  The outer arcs of blue nodes identifies first generation publications (citing\_sid) for each therapeutic. Nodes in the inner ring are sized by a gradient proportion to total degree count with an upper limit of 30 and are colored by a gradient proportional to the number of drug connections (2 to 5). 14  publications are common to all five networks (Table 3) and are colored red. The remaining nodes in the inner ring connect to between 2 and 4 drugs each and are labeled accordingly. Abbreviations: alem (Alemtuzumab), imat (Imatinib), nela (Nelarabine), ramu (Ramucirumab), suni(Sunitinib).}
\label{fig2}
%\end{adjustwidth}
\end{figure}

\end{document}

### 2017-12-05 LaTeX/Paper2/paper2.tex

@@
 
-\title{XX}
+\title{ERNIE: Supporting Collaboration Studies in Multiple Domains} 
 %\tnotetext[mytitlenote]{This document is a collaborative effort}
@@
 \author[nl]{Samet Keserci}
-
 \author[nl]{Avon Davey}
-
 \author[ca]{Di Cross}
-
 \author[gi]{Alexander R. Pico}
-
+\author[nl]{Dmitriy Korobskiy}
 \author[nl]{George Chacko \corref{cor1}}
@@
 \address[nl]{NETE Labs, NET ESolutions Corporation, McLean, VA, USA}
-\address[cal]{XX, USA}
+\address[ca]{XX, USA}
 \address[gi]{Gladstone Institutes, San Francisco, CA, USA}
@@
 \raggedright
+
 \begin{abstract}
+
+Data mining of public and commercially available data sources coupled with network analysis has been used as a digital methodology to document and analyze collaboration and knowledge flow in the development of a drug.
+This approach is extensible to research evaluation problems in any scientific area that can be defined by a nucleus of publications with accessible citation records.
+However, a tradeoff exists between exhaustive manual curation by experts and automated `big-data' methods.
+The former is less scalable, the latter can be less accurate.
+We have developed Enhanced Research Network Information Environment (ERNIE), a cloud-based knowledge platform that integrates free data drawn from public sources as well as licensed data from commercially available ones.
+ERNIE is built using Open Source tools, is easily replicated and modified, and its modular design enables the facile addition of new data sources and deletion or substitution of existing ones.
+Data in ERNIE can be accessed using search technologies or Structured Query Language (SQL).
+To demonstrate the capabilities of ERNIE we present the results of seven case studies that span drug development, pharmacogenomics, behavioral interventions, and opioid addiction.
+In these studies, we mine and analyze data from policy documents, regulatory approvals, research grants, bibliographic and patent databases as well as  clinical trials to document collaborations and identify influential research accomplishments.
+
 \end{abstract}
@@
 \section*{Results and Discussion} 
-\section*{Acknowledgments} This study would not have been possible without data that is made publicly available by NIH and the FDA.
-We thank Tandy Warnow from the University of Illinois Urbana-Champaign for critical comments and advice on formalizing definitions.
-We also thank Sandeep Somaiya and Syd Gomes from NETE as well as Holly J.
-Falk-Krzesinski, Daniel Calto, M'hamed Aisati, and Sherif El Shamy from Elsevier for their support of this collaboration.
+\section*{Acknowledgments} XX
 

### 2017-12-08 ExPORTER/Automation/column_extractor.py
exporter pipeline

@@ -1,0 +1,22 @@
+# column_extractor.py
+# this program is used to extract specific columns from the Reporter csv data
+# Date: 09/26/2017
+# Author: VJ Davey
+
+import pandas as pd
+import sys
+#reload(sys)
+#sys.setdefaultencoding('utf8')
+
+csv_file_path=str(sys.argv[1]); print 'Working with CSV file located at %s' %(csv_file_path)
+keep_headers = ['APPLICATION_ID','ACTIVITY','ADMINISTERING_IC','APPLICATION_TYPE','ARRA_FUNDED','AWARD_NOTICE_DATE','BUDGET_START',
+'BUDGET_END','CFDA_CODE','CORE_PROJECT_NUM','ED_INST_TYPE','FOA_NUMBER','FULL_PROJECT_NUM','SUBPROJECT_ID','FUNDING_ICs','FY','IC_NAME',
+'NIH_SPENDING_CATS','ORG_CITY','ORG_COUNTRY','ORG_DEPT','ORG_DISTRICT','ORG_DUNS','ORG_FIPS','ORG_NAME','ORG_STATE','ORG_ZIPCODE','PHR',
+'PI_IDS','PI_NAMEs','PROGRAM_OFFICER_NAME','PROJECT_START','PROJECT_END','PROJECT_TERMS','PROJECT_TITLE','SERIAL_NUMBER','STUDY_SECTION',
+'STUDY_SECTION_NAME','SUFFIX','SUPPORT_YEAR','TOTAL_COST','TOTAL_COST_SUB_PROJECT']
+df = pd.read_csv(csv_file_path, dtype=object, encoding='latin-1'); df = df[keep_headers];
+for header in keep_headers:
+    df[header] = df[header].str.replace(',','')
+    df[header] = df[header].str.encode('utf8')
+#df['PROJECT_TERMS'] = df['PROJECT_TERMS'].apply(lambda x: x.str[:18000])
+df.to_csv(csv_file_path[:-4]+'_EXTRACTED.csv', index=False)

### 2017-12-08 ExPORTER/Automation/exporter_update_auto.sh

@@ -1,0 +1,41 @@
+#RePORTER Project weekly updates
+
+# Author: VJ Davey
+# Date: 12/08/17
+
+# download the weekly RePORTER file and uncompress it
+c_dir=$1
+cd $c_dir
+
+last_week=$(cat $c_dir/counter)
+declare -i year=${last_week%_*}
+declare -i week=${last_week#*_}
+wget -q "https://exporter.nih.gov/CSVs/final/RePORTER_PRJ_C_FY${year}_$(printf "%03d" $week).zip" --no-check-certificate
+if [ $? -ne 0 ]; then
+  echo "Error: No CSV Download Available for year_week : ${year}_$(printf "%03d" $week)";
+  echo "Please perform a manual check of the Exporter website and manually update counter file if necessary"
+  exit 1;
+fi
+unzip $c_dir/*.zip; rm $c_dir/*.zip
+
+# pass the download to the python script to extract the proper columns, then copy the data into the temp table
+file=$(ls *.csv)
+python $c_dir/column_extractor.py $file; file_extract=$(echo $file | sed s/.csv/_EXTRACTED.csv/g); file_extract=${c_dir}${file_extract}
+# truncate the temp project table: temp_exporter_projects. Then update the table with data from the extract
+psql ernie -c "TRUNCATE TABLE temp_exporter_projects;"
+psql ernie -c "COPY temp_exporter_projects from '${file_extract}' delimiter ',' CSV HEADER;"
+# merge the temp table into the main table, update old records with new records based on pk match
+# insert on conflict update
[…]

### 2017-12-20 LaTeX/Paper2/paper2.tex
update

--- 2017-12-04 LaTeX/Paper2/paper2.tex
@@
 
-\title{XX}
+\title{ERNIE: Supporting Evaluation Studies in Multiple Domains} 
 %\tnotetext[mytitlenote]{This document is a collaborative effort}
@@
 \address[nl]{NETE Labs, NET ESolutions Corporation, McLean, VA, USA}
-\address[cal]{XX, USA}
+\address[ca]{Research Data Science \& Evaluation, Clarivate Analytics, USA}
 \address[gi]{Gladstone Institutes, San Francisco, CA, USA}
@@
 \raggedright
+
 \begin{abstract}
+
+Data mining of public and commercially available data sources coupled with network analysis has been successfully used as a digital methodology to document and evaluate research collaborations and knowledge flow associated with drug development.
+To support quantitative studies based on this approach, we have developed Enhanced Research Network Information Environment (ERNIE), a scalable cloud-based knowledge platform that integrates free data drawn from public sources as well as licensed data from commercially available ones.
+To facilitate adoption, reuse and extensibility, ERNIE was built using open source tools.
+A modular design enables the facile addition, deletion, or substitution of data sources and analytical workflows in ERNIE are partially automated to enable expert input at critical stages.
+To demonstrate the capabilities of ERNIE, we report the results of seven case studies that span drug development, pharmacogenomics, target discovery, behavioral interventions, and opioid addiction.
+In these studies, we mine and analyze data from policy documents, regulatory approvals, research grants, bibliographic and patent databases, and clinical trials, to document collaborations and identify influential research accomplishments.
+ERNIE is a template for repositories that can be used to support expert qualitative assessments, while offering burden reduction through automation and access to integrated data.
+
 \end{abstract}
@@
 \raggedright
-\section{Introduction}
 
-\section{Materials and Methods}
+\section*{Introduction}
+
+Research assessment is assisted by improved methods for data capture, new databases, and new scientific methods that offer burden reduction and enable the use of big-data and analysis at scale.
+Using data mining of administrative, regulatory, and scientific records coupled to network analysis, we have previously documented the scientific collaborations underlying the development of five FDA-approved therapeutics for cancer~\cite{Keserci2017}.
+Building upon prior work on single networks~\cite{Williams2015}, we have documented collaborations that extend across networks as well as records of the funding and peer review that sustain the system of scientific discovery.
+Analysis of such networks supports new insights into collaboration, knowledge diffusion, and recursive learning \textit{(supra vide)}.
+The framework used to mine data and integrate it into networks is flexible, can be automated, and adapted to a range of subjects  beyond drug development and can be used to support individual researchers, groups, and research organizations engaged in portfolio analysis and performance measurement.
+
+To further support such studies, we have developed Enhanced Research Network Informatics Environment (ERNIE), a cloud-based repository that integrates publicly available data as well as data from commercial sources.
+With continued reliance on a simple theme of data mining and network analysis, we have used the data within ERNIE to conduct seven case studies.
+The first two serve to validate ERNIE through reproducing the results of prior studies on ivacaftor and ipilimumab, breakthrough drugs used to treat cystic fibrosis and melanoma.
+The remaining case studies concern drugs used to treat opioid addiction, a microarray system for pharmacogenomic profiling, a target discovery system based on enzyme fragment complementation assays, and a behavioral intervention for substance abuse.
+The datasets that result from these studies are made available for use by other researchers and the workflows used to generate them are also archived to permit reproduction of our results, as well as review and modification of the methods used to generate them.
+
+\section*{Materials and Methods}
+
+\emph{Infrastructure} Cloud computing has evolved to the point where computing services and storage are widely available at affordable prices.
+We prototyped ERNIE as a PostgreSQL 9.6 database in a CentOS 7.4 virtual machine hosted in the Microsoft Azure cloud.
+A second virtual machine has Apache Solr x.y installed and is used to enable fast text based searches of the data in ERNIE.
+Both these virtual machines are located in a secure address space that is accessible only to authorized users.
+Automated processes managed through the Jenkins Continuous Integration server use custom ETL processes wto load these data into the ERNIE schema and refresh them periodically.
+The scripts that are written for these ETL processes are available on a Github site.
+\emph{[Need some text from DK and Avon!]}
+
+\emph{Data Sources} Data in ERNIE are derived from publicly available and commercial sources.
+Publicly available data are copied from the National Clinical Trials Database, the FDA Orange and Purple Books,  the United States Patent Office, and NIH ExPORTER.
+Leased data are acquired from Clarivate Analytics In and consist of the Web of Science Core Collection and the Derwent Patent Citation Index.
+Custom ETL processes were developed to load these data into the ERNIE schema and refresh them periodically.
+The scripts that are written for these ETL processes are available on a Github site.
+
+\emph{Data Mining and Digitization}
+
+\emph{Amplification}
+
+\emph{Network Calculations}
+
+\emph{Visualizations}
 
 \section*{Results and Discussion} 
-\section*{Acknowledgments} This study would not have been possible without data that is made publicly available by NIH and the FDA.
-We thank Tandy Warnow from the University of Illinois Urbana-Champaign for critical comments and advice on formalizing definitions.
-We also thank Sandeep Somaiya and Syd Gomes from NETE as well as Holly J.
-Falk-Krzesinski, Daniel Calto, M'hamed Aisati, and Sherif El Shamy from Elsevier for their support of this collaboration.
+\section*{Acknowledgments} Research and development reported in this publication was supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract No.
+HHSN271201700053C.
+The content of this publication is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
+\cite{LeidenManifesto2015}
 
-\section{References}
+\section*{References}
 
-\begin{thebibliography}{10}
-\raggedright
-
-\bibitem{bibWilliams}
-Williams RS, Lotia S, Holloway AK, Pico AR.
-\newblock {{F}rom Scientific Discovery to Cures: Bright Stars within a Galaxy.}
-\newblock Cell. 2015 163:21-23. doi: 10.1016/j.cell.2015.09.007
-
-\end{thebibliography}
+\bibliography{chacko}
 

### 2017-12-22 Analysis/Network_Analyzer/AuthorScores.java
network analyzer scripts

@@ -1,0 +1,209 @@
+import java.io.BufferedReader;
+import java.io.FileNotFoundException;
+import java.io.FileReader;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.text.DecimalFormat;
+import java.util.*;
+
+public class AuthorScores {
+
+	MainDriver dirs = new MainDriver();
+
+	
+	
+	public static void test(){
+		System.out.println("TESET");
+	}
+
+	public HashMap<String, Integer> author_totalCitation(String refType) throws IOException {
+		HashMap<String, Integer> out = new HashMap<String, Integer>();
+
+		Mappers mappers = new Mappers();
+		PaperScores paperscores = new PaperScores();
+		HashMap<String, HashSet<String>> auth_pubSet_MAP = mappers.auth_pubSet_MAP(refType);
+		HashMap<String, Integer> pub_citation = paperscores.pub_citation_MAP(refType);
+
+		for (String auth : auth_pubSet_MAP.keySet()) {
+
+			int sum = 0;
+
+			for (String pub : auth_pubSet_MAP.get(auth)) {
+				sum += pub_citation.get(pub);
+			}
+
+			out.put(auth, sum);
+
+		}
+		
+		return out;
+	}
+
+	public HashMap<String, Integer> author_PIR(String refType) throws IOException {
+
+		HashMap<String, Integer> out = new HashMap<String, Integer>();
+
+		Mappers mappers = new Mappers();
+		PaperScores paperscores = new PaperScores();
+
+		HashMap<String, HashSet<String>> auth_pubSet_MAP = mappers.auth_pubSet_MAP(refType);
+		HashMap<String, Integer> pub_weighted_citation = paperscores.pub_WeigtedCitation_MAP(refType);
+
+		for (String auth : auth_pubSet_MAP.keySet()) {
+
+			int sum = 0;
+
+			for (String pub : auth_pubSet_MAP.get(auth)) {
+				sum += pub_weighted_citation.get(pub);
+			}
+
+			out.put(auth, sum);
+
+		}
+
+		return out;
+	}
+
+	public HashMap<String, Integer> author_inDegree(String refType) throws IOException {
+
+		HashMap<String, Integer> out = new HashMap<String, Integer>();
+
+		Mappers mappers = new Mappers();
+
+		HashMap<String, HashSet<String>> auth_pubSet_MAP = mappers.auth_pubSet_MAP(refType);
+
+		for (String auth : auth_pubSet_MAP.keySet()) {
+
[…]

### 2017-12-22 Analysis/Network_Analyzer/MASTER_DRIVER.sh

@@ -1,0 +1,26 @@
+
+
+
+
+if [ $# != 3 ]
+then
+  echo -e "\n\n**************************************************************************"
+  echo -e     "***** ERROR : Missing drug name, input directory or output directory *****"
+  echo -e "Usage :\nsh MasterDriver.sh <drugname> <input_dir> <output_dir>"
+  echo -e "Please provide drugname, input_dir, and output_dir"
+  echo -e "Allowed drug or device names are: \naffymetrix, ipilimumab, ivacaftor, buprenorphine, discoverx, lifeskills, naltrexone"
+  echo -e "Sample Usage:\nshMasterDriver.sh affymetrix <directory to your input files> <directory to output files> "
+  exit
+fi
+
+
+drug_device_name=$1 # must be given
+input_dir=$2 # must be given
+output_dir=$3 # must be given
+
+
+javac *.java
+
+java MainDriver $drug_device_name $input_dir $output_dir
+
+rm $output_dir/stat_collector.txt

### 2017-12-22 Analysis/Network_Analyzer/Mappers.java

@@ -1,0 +1,545 @@
+import java.io.BufferedReader;
+import java.io.FileNotFoundException;
+import java.io.FileReader;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.util.*;
+
+public class Mappers {
+
+	MainDriver dirs = new MainDriver();
+
+	// set of all publication based on wos_id in the network
+	public HashSet<String> pub_SET(String refType) throws IOException {
+
+		HashSet<String> out = new HashSet<String>();
+
+		FileReader reader = new FileReader(dirs.getInputDir() + dirs.getDrugName() + "_citation_network.txt");
+		BufferedReader br = new BufferedReader(reader);
+
+		int ref_col = 0;
+		int cited_ref_col = 0;
+
+		if (refType.equals("pmid")) {
+			ref_col = 0;
+			cited_ref_col = 3;
+		} else if (refType.equals("wos")) {
+			ref_col = 1;
+			cited_ref_col = 2;
+		} else {
+
+			System.out.println(" Reference Type must be either 'pmid' or 'wos' ");
+			return null;
+		}
+
+		String header_ref_cited_ref = br.readLine();
+
+		// Reading text line by line
+		String ref_cited_ref = br.readLine();
+
+		int edge_count = 0;
+		while (ref_cited_ref != null) {
+
+			String[] ref_cited_ref_arr = ref_cited_ref.split("\t");
+
+			if (!ref_cited_ref_arr[ref_col].equals("NA"))
+				out.add(ref_cited_ref_arr[ref_col]);
+			if (!ref_cited_ref_arr[cited_ref_col].equals("NA"))
+				out.add(ref_cited_ref_arr[cited_ref_col]);
+
+			if (!ref_cited_ref_arr[ref_col].equals("NA") && !ref_cited_ref_arr[cited_ref_col].equals("NA")) {
+				++edge_count;
+			}
+
+			ref_cited_ref = br.readLine();
+
+		}
+
+		reader.close();
+
+		System.out.println("pub_size based on " + refType + " " + out.size() + "\n");
+		// System.out.println(out);
+
+		FileWriter stat_collector = new FileWriter(dirs.getFinalDir() + "/stat_collector.txt", true);
+		stat_collector.write(dirs.getDrugName() + "_pub_size based on " + refType + " " + out.size() + "\n");
[…]

### 2017-12-22 Analysis/Network_Analyzer/PaperScores.java

@@ -1,0 +1,183 @@
+
+import java.io.BufferedReader;
+import java.io.FileNotFoundException;
+import java.io.FileReader;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.text.DecimalFormat;
+import java.util.*;
+
+public class PaperScores {
+	
+	MainDriver dirs = new MainDriver();
+
+	// publication citation, if no citation then it is by default 0.
+	public HashMap<String, Integer> pub_citation_MAP(String refType) throws IOException {
+
+		HashMap<String, Integer> out = new HashMap<String, Integer>();
+		Mappers mappers = new Mappers();
+		HashMap<String, HashSet<String>> pub_citingPubSet_Map = mappers.pub_citingPubSET_MAP(refType);
+		HashSet<String> pubSet = mappers.pub_SET(refType);
+		int max_citation = 0;
+
+		for (String pub : pubSet) {
+			if (pub_citingPubSet_Map.containsKey(pub)) {
+				int cit = pub_citingPubSet_Map.get(pub).size();
+				max_citation = (max_citation > cit) ? max_citation : cit;
+				out.put(pub, cit);
+			} else {
+				out.put(pub, 0);
+			}
+
+		}
+
+		System.out.println();
+		System.out.println(out.size() + " " + pub_citingPubSet_Map.size() + " " + pubSet.size());
+		System.out.println(dirs.getDrugName() + "max_citation based on " + refType + ": " + max_citation + "\n");
+
+		FileWriter stat_collector = new FileWriter(dirs.getFinalDir() + "/stat_collector.txt", true);
+		stat_collector.write(dirs.getDrugName() + "_max_citation based on " + refType + ": " + max_citation + "\n");
+		stat_collector.close();
+
+		return out;
+
+	}
+
+	public HashMap<String, Integer> pub_WeigtedCitation_MAP(String refType) throws IOException {
+
+		HashMap<String, Integer> out = new HashMap<String, Integer>();
+		Mappers mappers = new Mappers();
+		HashMap<String, HashSet<String>> pub_citingPubSet_Map = mappers.pub_citingPubSET_MAP(refType);
+		HashMap<String, Integer> pub_citation_map = pub_citation_MAP(refType);
+		int max_weightedcitation = 0;
+
[…]

### 2017-12-25 LaTeX/Paper2/paper2.tex
revised introduction

@@
 
-\title{ERNIE: Supporting Evaluation Studies in Multiple Domains} 
+\title{ERNIE: Accessible Support for Research Assessment} 
 %\tnotetext[mytitlenote]{This document is a collaborative effort}
@@
 To support quantitative studies based on this approach, we have developed Enhanced Research Network Information Environment (ERNIE), a scalable cloud-based knowledge platform that integrates free data drawn from public sources as well as licensed data from commercially available ones.
-To facilitate adoption, reuse and extensibility, ERNIE was built using open source tools.
-A modular design enables the facile addition, deletion, or substitution of data sources and analytical workflows in ERNIE are partially automated to enable expert input at critical stages.
+To facilitate adoption, reuse and extensibility, ERNIE was built with open source tools.
+and a modular design enables the facile addition, deletion, or substitution of data sources.
+Analytical workflows in ERNIE are partially automated to enable expert input at critical stages.
 To demonstrate the capabilities of ERNIE, we report the results of seven case studies that span drug development, pharmacogenomics, target discovery, behavioral interventions, and opioid addiction.
@@
 
-Research assessment is assisted by improved methods for data capture, new databases, and new scientific methods that offer burden reduction and enable the use of big-data and analysis at scale.
-Using data mining of administrative, regulatory, and scientific records coupled to network analysis, we have previously documented the scientific collaborations underlying the development of five FDA-approved therapeutics for cancer~\cite{Keserci2017}.
-Building upon prior work on single networks~\cite{Williams2015}, we have documented collaborations that extend across networks as well as records of the funding and peer review that sustain the system of scientific discovery.
+Given the risk of the research evaluation being driven by data and metrics without sufficiently considering balanced judgment, sound principles have been articulated to advise its practice~\cite{LeidenManifesto2015}.
+However, data are still critical and utilitarian approaches for capture, integration, and archival that offer coverage and burden reduction assist the practice of research evaluation especially when coupled with improved analytical methods.
+While bibliographic data is usually central to research evaluation, the use of administrative records such federal government statistics and those of research institutions and research funders can be valuable as a supplemental source~\cite{FedStat2017}.
+
+Using data mining of publicly available administrative, regulatory, and scientific records and network analysis, Williams and colleagues defined relationships between scientific discoveries and major advances in medicine such as new drugs~\cite{Williams2015}.
+Extending this work, we have previously documented the scientific collaborations that extend across networks underlying the development of five independently developed therapeutics for cancer~\cite{Keserci2017}.
 Analysis of such networks supports new insights into collaboration, knowledge diffusion, and recursive learning \textit{(supra vide)}.
-The framework used to mine data and integrate it into networks is flexible, can be automated, and adapted to a range of subjects  beyond drug development and can be used to support individual researchers, groups, and research organizations engaged in portfolio analysis and performance measurement.
+The framework we developed to mine data and integrate it into networks for analysis has the benefit of retaining expert inputis flexible but can be further automated, adapted to a range of subjects beyond drug development, and used to support individual researchers, groups, and research organizations engaged in research assessments.
+In pursuit of these objectives we have developed Enhanced Research Network Informatics Environment (ERNIE), a knowledge platform that integrates publicly available data as well as data from commercial sources.
+Since cloud computing has evolved to the point where scalable computing services and storage are accessible to a broad user population, ERNIE was designed to exist as a cloud resource.
 
-To further support such studies, we have developed Enhanced Research Network Informatics Environment (ERNIE), a cloud-based repository that integrates publicly available data as well as data from commercial sources.
-With continued reliance on a simple theme of data mining and network analysis, we have used the data within ERNIE to conduct seven case studies.
-The first two serve to validate ERNIE through reproducing the results of prior studies on ivacaftor and ipilimumab, breakthrough drugs used to treat cystic fibrosis and melanoma.
+Focusing on the theme of data mining and network analysis, we have used the data within ERNIE to conduct seven case studies.
+In these studies, we mine and analyze data from policy documents, regulatory approvals, research grants, bibliographic and patent databases, and clinical trials, to document collaborations and identify influential research accomplishments.
+The workflows used incorporate expert knowledge into defining a set of core documents from which citations can be extracted, linked to other records in ERNIE, and analyzed.
+The first two case studies serve to validate ERNIE through reproducing the results of prior studies on ivacaftor and ipilimumab, breakthrough drugs used to treat cystic fibrosis and melanoma~\cite{Williams2015}.
 The remaining case studies concern drugs used to treat opioid addiction, a microarray system for pharmacogenomic profiling, a target discovery system based on enzyme fragment complementation assays, and a behavioral intervention for substance abuse.
@@
 
-\emph{Infrastructure} Cloud computing has evolved to the point where computing services and storage are widely available at affordable prices.
-We prototyped ERNIE as a PostgreSQL 9.6 database in a CentOS 7.4 virtual machine hosted in the Microsoft Azure cloud.
-A second virtual machine has Apache Solr x.y installed and is used to enable fast text based searches of the data in ERNIE.
-Both these virtual machines are located in a secure address space that is accessible only to authorized users.
-Automated processes managed through the Jenkins Continuous Integration server use custom ETL processes wto load these data into the ERNIE schema and refresh them periodically.
-The scripts that are written for these ETL processes are available on a Github site.
+\emph{Infrastructure} ERNIE exists as two Centos 7.4 virtual machines in the Microsoft Azure cloud with 10 terabytes of attached storage.
+One virtual machine,  standard D8s v3 (8 vcpu, 32 Gb), houses data in a PostgreSQL 9.6 database.
+A second virtual machine, a standard DS4 (8 vcpu, 28 Gb), has Apache Solr 7.x installed and is used to enable fast text based searches of the data in ERNIE.
+Automated processes are managed through the Jenkins Continuous Integration server and use custom ETL processes in Python to load and refresh data into the ERNIE schema.
+Secure access is managed through multiple factor authentication.
+Ssh tunnels are used to facilitate communications between virtual machines.
+Specifications, deployment scripts, and ETL scripts are available on a Github site~\cite{GithubERNIE2017}.
 \emph{[Need some text from DK and Avon!]}
 
-\emph{Data Sources} Data in ERNIE are derived from publicly available and commercial sources.
+\emph{Data sources} Data in ERNIE are derived from publicly available and commercial sources.
 Publicly available data are copied from the National Clinical Trials Database, the FDA Orange and Purple Books,  the United States Patent Office, and NIH ExPORTER.
-Leased data are acquired from Clarivate Analytics In and consist of the Web of Science Core Collection and the Derwent Patent Citation Index.
-Custom ETL processes were developed to load these data into the ERNIE schema and refresh them periodically.
-The scripts that are written for these ETL processes are available on a Github site.
+Leased data are acquired from Clarivate Analytics and consist of the Web of Science Core Collection and the Derwent Patent Citation Index.
+The data in ERNIE are stored in a relational schema that is also documented in Github.
 
-\emph{Data Mining and Digitization}
+\emph{Data mining and digitization} A set of source documents relevant to the question being asked is assembled and mined for citations to scientific literature using manual or semi-manual methods.
+Manual extraction involved searching for text strings that represent references of interest and matching those to unique identifiers in PubMed and/or Web of Science.
+As an example, the medical review document relevant to approval of ipilimumab contained X references.
+Y of them were matched to PubMed identifiers using the PubMed either through its web interface or the E-utils API.
+This process was modified to take advantage of the Solr search engine.
 
@@
 The content of this publication is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
-\cite{LeidenManifesto2015}
 

### 2017-12-26 LaTeX/Paper2/paper2.tex
update

--- 2017-12-05 LaTeX/Paper2/paper2.tex
@@
 
-\title{ERNIE: Supporting Collaboration Studies in Multiple Domains} 
+\title{ERNIE: A Knowledge Platform to Support Research Assessment} 
 %\tnotetext[mytitlenote]{This document is a collaborative effort}
@@
 \address[nl]{NETE Labs, NET ESolutions Corporation, McLean, VA, USA}
-\address[ca]{XX, USA}
+\address[ca]{Research Data Science \& Evaluation, Clarivate Analytics, USA}
 \address[gi]{Gladstone Institutes, San Francisco, CA, USA}
@@
 
-Data mining of public and commercially available data sources coupled with network analysis has been used as a digital methodology to document and analyze collaboration and knowledge flow in the development of a drug.
-This approach is extensible to research evaluation problems in any scientific area that can be defined by a nucleus of publications with accessible citation records.
-However, a tradeoff exists between exhaustive manual curation by experts and automated `big-data' methods.
-The former is less scalable, the latter can be less accurate.
-We have developed Enhanced Research Network Information Environment (ERNIE), a cloud-based knowledge platform that integrates free data drawn from public sources as well as licensed data from commercially available ones.
-ERNIE is built using Open Source tools, is easily replicated and modified, and its modular design enables the facile addition of new data sources and deletion or substitution of existing ones.
-Data in ERNIE can be accessed using search technologies or Structured Query Language (SQL).
-To demonstrate the capabilities of ERNIE we present the results of seven case studies that span drug development, pharmacogenomics, behavioral interventions, and opioid addiction.
-In these studies, we mine and analyze data from policy documents, regulatory approvals, research grants, bibliographic and patent databases as well as  clinical trials to document collaborations and identify influential research accomplishments.
+Data mining of public and commercially available data sources coupled with network analysis has been successfully used as a digital methodology to study research collaborations and knowledge flow associated with drug development.
+To enable quantitative studies based on this approach, we have developed Enhanced Research Network Information Environment (ERNIE), a scalable cloud-based knowledge platform that integrates free data drawn from public sources as well as licensed data from commercially available ones.
+Analytical workflows in ERNIE are partially automated to enable expert input at critical stages.
+To facilitate adoption, reuse and extensibility, ERNIE was built with open source tools.
+and a modular design enables the facile addition, deletion, or substitution of data sources.
+To demonstrate the capabilities of ERNIE, we report the results of seven case studies that span drug development, pharmacogenomics, target discovery, behavioral interventions, and opioid addiction.
+In these studies, we mine and analyze data from policy documents, regulatory approvals, research grants, bibliographic and patent databases, and clinical trials, to document collaborations and identify influential research accomplishments.
+ERNIE is a template for repositories that can be used to support expert qualitative assessments, while offering burden reduction through automation and access to integrated data.
 
@@
 \raggedright
-\section{Introduction}
 
-\section{Materials and Methods}
+\section*{Introduction}
+
+The risk of research evaluation being driven by data and metrics with insufficient consideration of balanced judgment has driven the formulation of  sound principles to advise practice~\cite{LeidenManifesto2015}.
+However, data are still critical for evaluation, and utilitarian approaches for capture, integration, and archival that offer coverage and burden reduction assist the practice of research evaluation.
+While bibliographic data is usually central to research evaluation, the use of administrative records such as government statistics and research funding offers complementary value~\cite{FedStat2017}.
+
+Using data mining of publicly available administrative, regulatory, and scientific records and network analysis, Williams and colleagues defined relationships between scientific discoveries and major advances in medicine such as new drugs~\cite{Williams2015}.
+Extending this work, we have previously documented the scientific collaborations that extend across networks underlying the development of five independently developed therapeutics for cancer~\cite{Keserci2017}.
+Analysis of such networks supports new insights into collaboration, knowledge diffusion, and recursive learning \textit{(vide supra)}.
+The framework we developed to mine data and integrate it into networks for analysis incorporates expert input, is flexible, can be further automated, adapted to a range of subjects beyond drug development, and used to support individual researchers, groups, and research organizations engaged in research assessment.
+In addition, cloud computing and data science have evolved to the point where scalable computing services and analytical methods are accessible to a broad user population.
+Thus, we have developed Enhanced Research Network Informatics Environment (ERNIE), a knowledge platform that integrates publicly available data as well as data from commercial sources.
+
+In demonstration that is focused on the theme of data mining and network analysis, we have used the data within ERNIE to conduct seven case studies.
+In these studies, we mine and analyze data from policy documents, regulatory approvals, research grants, bibliographic and patent databases, and clinical trials, to document collaborations and identify influential research accomplishments.
+The workflows used incorporate expert knowledge into defining a set of core documents from which citations can be extracted, linked to other records in ERNIE, and analyzed.
+The first two case studies serve to validate ERNIE through reproducing the results of prior studies~\cite{Williams2015} on ivacaftor and ipilimumab, breakthrough drugs used to treat cystic fibrosis and melanoma.
+The remaining case studies concern drugs used to treat opioid addiction~\cite{Blumberg1973,Cowan1977} , a microarray system for pharmacogenomic profiling~\cite{deLeon2006}, a target discovery system originating from enzyme fragment complementation assays~\cite{Khanna1989}, and a behavioral intervention for substance abuse~\cite{Botvin1980}.
+The datasets that result from these studies are made available for use by other researchers and the workflows used to generate them are also archived to permit reproduction of our results, as well as review and modification of the methods used to generate them.
+
+\section*{Materials and Methods}
+
+\emph{Infrastructure} ERNIE exists as two CentOS 7.4 virtual machines in the Microsoft Azure cloud with 10 terabytes of attached storage.
+One virtual machine, standard D8s v3 (8 vcpu, 32 Gb), houses the main database within a PostgreSQL 9.6 server, and additionally acts as a central hub for data related processes.
+A second virtual machine, standard DS4 (8 vcpu, 28 Gb), houses an installation of Apache Solr 7.1 that is used to create and store indexes of data relevant to ERNIE.
+Access to both virtual machines is made secure through use of multiple-factor authentication, with a unique time-based code verification acting as one of the key factors.
+SSH tunnels are used for communication between virtual machines and automated processes for ERNIE are managed through a Jenkins Continuous Integration server.
+Custom ETL processes mostly consisting of Bash, Python, and SQL scripts are pulled from the project Github repository~\cite{GithubERNIE2017} and deployed via Jenkins in order to load and refresh data from several sources.
+
+\emph{Data sources} Data in ERNIE are derived from both publicly available and commercial sources.
+Publicly available data are copied from the National Clinical Trials Database \cite,  the FDA Orange and Purple Books \cite,  the United States Patent Office \cite, and NIH ExPORTER \cite.
+Leased data are acquired from Clarivate Analytics and consist of the Web of Science Core Collection and the Derwent World Patent Index~\cite{DWPI2017}.
+The data in ERNIE are stored in a relational schema that is also documented in Github.
+\emph{[Need some text from DK and Avon!]}
+
+\emph{Workflows} The core workflow in ERNIE consists of (i) Source document identification, in which a set of source documents relevant to the question being asked is assembled  (ii) Citation extraction, in which text references to scientific publications and patents are matched to unique identifiers such as PubMed ID, UT (Web of Science Accession Number), or US patent number.
+(iii) Amplification, in which publications and patents linked by citation to extracted references are identified through citation records in the Web of Science (iv) Network analysis, in which the data assembled through the preceding stages are represented as a network and influential nodes are identified (v) Visualization of the network data to provide insight and stimulate further investigation.
+
+\emph {Source document identification}
+
+\emph {Citation extraction} Input and end product
+
+\emph {Amplification} What is the input and end product
+
+\emph{Network analysis} Input and end product
+
+\emph{Visualizations} Input and end product
 
 \section*{Results and Discussion}
-\section*{Acknowledgments} XX
 
-\section{References}
+\section*{Acknowledgments} Research and development reported in this publication was supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract No.
+HHSN271201700053C.
+The content of this publication is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
 
-\begin{thebibliography}{10}
-\raggedright
+\section*{References}
 
-\bibitem{bibWilliams}
-Williams RS, Lotia S, Holloway AK, Pico AR.
-\newblock {{F}rom Scientific Discovery to Cures: Bright Stars within a Galaxy.}
-\newblock Cell. 2015 163:21-23. doi: 10.1016/j.cell.2015.09.007
-
-\end{thebibliography}
+\bibliography{chacko}
 

### 2017-12-26 LaTeX/Paper2/paper2.tex
Paper updates

--- 2017-12-25 LaTeX/Paper2/paper2.tex
@@
 Analysis of such networks supports new insights into collaboration, knowledge diffusion, and recursive learning \textit{(supra vide)}.
-The framework we developed to mine data and integrate it into networks for analysis has the benefit of retaining expert inputis flexible but can be further automated, adapted to a range of subjects beyond drug development, and used to support individual researchers, groups, and research organizations engaged in research assessments.
+The framework we developed to mine data and integrate it into networks for analysis has the benefit of retaining expert input is flexible but can be further automated, adapted to a range of subjects beyond drug development, and used to support individual researchers, groups, and research organizations engaged in research assessments.
 In pursuit of these objectives we have developed Enhanced Research Network Informatics Environment (ERNIE), a knowledge platform that integrates publicly available data as well as data from commercial sources.
@@
 
-\emph{Infrastructure} ERNIE exists as two Centos 7.4 virtual machines in the Microsoft Azure cloud with 10 terabytes of attached storage.
-One virtual machine,  standard D8s v3 (8 vcpu, 32 Gb), houses data in a PostgreSQL 9.6 database.
-A second virtual machine, a standard DS4 (8 vcpu, 28 Gb), has Apache Solr 7.x installed and is used to enable fast text based searches of the data in ERNIE.
-Automated processes are managed through the Jenkins Continuous Integration server and use custom ETL processes in Python to load and refresh data into the ERNIE schema.
-Secure access is managed through multiple factor authentication.
-Ssh tunnels are used to facilitate communications between virtual machines.
-Specifications, deployment scripts, and ETL scripts are available on a Github site~\cite{GithubERNIE2017}.
-\emph{[Need some text from DK and Avon!]}
+\emph{Open Source} All ERNIE code is open-source under the MIT license and available on GitHub ~\cite{GithubERNIE2017}.
 
-\emph{Data sources} Data in ERNIE are derived from publicly available and commercial sources.
-Publicly available data are copied from the National Clinical Trials Database, the FDA Orange and Purple Books,  the United States Patent Office, and NIH ExPORTER.
+\emph{Infrastructure} ERNIE runs on two CentOS 7.4 Linux servers in the Microsoft Azure cloud with 10 terabytes of
+attached storage.
+One server, Azure standard D8s v3 (8 VCPUs, 32 Gb RAM), hosts data in a PostgreSQL 9.6 relational database, and
+additionally acts as a central hub for data related processes.
+A second server, an Azure standard DS4 (8 VCPUs, 28 Gb), runs Apache Solr 7.x search server, which is used to to create
+and store indexes of ERNIE data to facilitate fast free-text user searches.
+Access to ERNIE servers is secured through SSH tunneling and two-factor authentication, with a unique time-based code
+acting as one of the factors.
+
+Automated ERNIE processes are managed by the Jenkins Continuous Integration server.
+Custom Extract-Transform-Load (ETL) scripts are developed in Bash, Python, Java and SQL.
+Jenkins is additionally used to deploy scripts dedicated to data transformation and perform other
+calculations.
+In that regard, Jenkins is used to direct construction of Solr indexes as new data is introduced into
+ERNIE, as well as the construction of citation networks for specified topics.
+The Solr indexes can handle varying forms of Lucene-based search and full-text search, and may quickly return
+informative, ranked, and scored query results so that a user may be able to map data across sources.
+The citation networks are sub-networks (based largely in the Web of Science) that are generated based upon user input
+and subsequently analyzed.
+
+\emph{Data sources} Data in ERNIE are extracted from publicly available and commercial sources.
+Publicly available data are extracted from the National Clinical Trials Database, the FDA Orange and Purple Books, the United States Patent Office, and NIH ExPORTER.
 Leased data are acquired from Clarivate Analytics and consist of the Web of Science Core Collection and the Derwent Patent Citation Index.
-The data in ERNIE are stored in a relational schema that is also documented in Github.
+The data in ERNIE are stored in a relational schema that is documented.
+Documentation is available on GitHub.
 
-\emph{Data mining and digitization} A set of source documents relevant to the question being asked is assembled and mined for citations to scientific literature using manual or semi-manual methods.
+\emph{Data architecture and governance} ERNIE is aiming to provide data of best possible quality to
+its analysts and users.
+ERNIE data is extracted from several upstream sources of varying quality hence the need to cleanse
+data.
+ERNIE's approach to cleansing is to prefer data quality and normalized data over data completeness.
+The following are key aspects of ERNIE's data architecture and governance:
+\begin{itemize}
+  \item De-duplication.
+De-duplication is a process of eliminating logically duplicate records, that is records with
+identical primary or unique keys.
+In ERNIE duplicate records from such a group are deleted while leaving in place a single
+representative record (preferring a record which is updated last).
+An alternative de-duplication strategy could be to aggregate differing non-key fields from logical
+duplicates into lists.
+  \item Normalization.
+After data is de-duplicated, the next step in data normalization is to establish foreign key
+relationships between children and parent entities and eliminate orphans: child records with
+non-existing parents.
+In ERNIE orphan records are deleted.
+An alternative normalization strategy could be to segregate orphans logically or physically while
+creating parent stub records.
+  \item Schema Permanence.
+In order to improve availability of data and simplify data schema management, ERNIE ETL scripts are
+designed to avoid recreating of main entities, for example, by using TRUNCATE TABLE instead of table re-creation.
+  \item Data Stewardship.
+ERNIE data stewards are people responsible for quality of a particular data subject area.
+Data stewards get notified when a data issue is detected and drive the workflows necessary for data
+issue remediation.
+They are also typically responsible for communicating changes in data structures.
+\end{itemize}
+
+\emph{Data mining and digitization} A set of source documents relevant to the question being asked is assembled and mined for citations to scientific literature using manual or semi-automated methods.
 Manual extraction involved searching for text strings that represent references of interest and matching those to unique identifiers in PubMed and/or Web of Science.
@@
 Y of them were matched to PubMed identifiers using the PubMed either through its web interface or the E-utils API.
-This process was modified to take advantage of the Solr search engine.
+ERNIE is designed to support semi-automated case studies.
 

### 2017-12-26 LaTeX/Paper2/paper2.tex

--- 2017-12-26 LaTeX/Paper2/paper2.tex
@@
 Extending this work, we have previously documented the scientific collaborations that extend across networks underlying the development of five independently developed therapeutics for cancer~\cite{Keserci2017}.
-Analysis of such networks supports new insights into collaboration, knowledge diffusion, and recursive learning \textit{(vide supra)}.
-The framework we developed to mine data and integrate it into networks for analysis incorporates expert input, is flexible, can be further automated, adapted to a range of subjects beyond drug development, and used to support individual researchers, groups, and research organizations engaged in research assessment.
+Analysis of such networks supports new insights into collaboration, knowledge diffusion, and recursive learning \textit{( videsupra)}.
+The framework we developed to mine data and integrate it into networks for analysis incorporates expert input, is flexible , can be further automated, adapted to a range of subjects beyond drug development, and used to support individual researchers, groups, and research organizations engaged in research assessment.
 In addition, cloud computing and data science have evolved to the point where scalable computing services and analytical methods are accessible to a broad user population.
@@
 
-\emph{Infrastructure} ERNIE exists as two CentOS 7.4 virtual machines in the Microsoft Azure cloud with 10 terabytes of attached storage.
-One virtual machine, standard D8s v3 (8 vcpu, 32 Gb), houses the main database within a PostgreSQL 9.6 server, and additionally acts as a central hub for data related processes.
-A second virtual machine, standard DS4 (8 vcpu, 28 Gb), houses an installation of Apache Solr 7.1 that is used to create and store indexes of data relevant to ERNIE.
-Access to both virtual machines is made secure through use of multiple-factor authentication, with a unique time-based code verification acting as one of the key factors.
-SSH tunnels are used for communication between virtual machines and automated processes for ERNIE are managed through a Jenkins Continuous Integration server.
-Custom ETL processes mostly consisting of Bash, Python, and SQL scripts are pulled from the project Github repository~\cite{GithubERNIE2017} and deployed via Jenkins in order to load and refresh data from several sources.
+\emph{Open Source} All ERNIE code is open-source under the MIT license and available on GitHub ~\cite{GithubERNIE2017}.
 
-\emph{Data sources} Data in ERNIE are derived from both publicly available and commercial sources.
+\emph{Infrastructure} ERNIE runs on two CentOS 7.4 Linux servers in the Microsoft Azure cloud with 10 terabytes of
+attached storage.
+One server, Azure standard D8s v3 (8 VCPUs, 32 Gb RAM), hosts data in a PostgreSQL 9.6 relational database, and
+additionally acts as a central hub for data related processes.
+A second server, an Azure standard DS4 (8 VCPUs, 28 Gb), runs Apache Solr 7.x search server, which is used to to create
+and store indexes of ERNIE data to facilitate fast free-text user searches.
+Access to ERNIE servers is secured through SSH tunneling and two-factor authentication, with a unique time-based code
+acting as one of the factors.
+
+Automated ERNIE processes are managed by the Jenkins Continuous Integration server.
+Custom Extract-Transform-Load (ETL) scripts are developed in Bash, Python, Java and SQL.
+Jenkins is additionally used to deploy scripts dedicated to data transformation and perform other
+calculations.
+In that regard, Jenkins is used to direct construction of Solr indexes as new data is introduced into
+ERNIE, as well as the construction of citation networks for specified topics.
+The Solr indexes can handle varying forms of Lucene-based search and full-text search, and may quickly return
+informative, ranked, and scored query results so that a user may be able to map data across sources.
+The citation networks are sub-networks (based largely in the Web of Science) that are generated based upon user input
+and subsequently analyzed.
+
+\emph{Data sources} Data in ERNIE are extracted from both publicly available and commercial sources.
 Publicly available data are copied from the National Clinical Trials Database \cite,  the FDA Orange and Purple Books \cite,  the United States Patent Office \cite, and NIH ExPORTER \cite.
 Leased data are acquired from Clarivate Analytics and consist of the Web of Science Core Collection and the Derwent World Patent Index~\cite{DWPI2017}.
-The data in ERNIE are stored in a relational schema that is also documented in Github.
-\emph{[Need some text from DK and Avon!]}
+The data in ERNIE are stored in a relational schema that is documented.
+Documentation is available on GitHub.
+
+\emph{Data architecture and governance} ERNIE is aiming to provide data of best possible quality to
+its analysts and users.
+ERNIE data is extracted from several upstream sources of varying quality hence the need to cleanse
+data.
+ERNIE's approach to cleansing is to prefer data quality and normalized data over data completeness.
+The following are key aspects of ERNIE's data architecture and governance:
+\begin{itemize}
+  \item De-duplication.
+De-duplication is a process of eliminating logically duplicate records, that is records with
+identical primary or unique keys.
+In ERNIE duplicate records from such a group are deleted while leaving in place a single
+representative record (preferring a record which is updated last).
+An alternative de-duplication strategy could be to aggregate differing non-key fields from logical
+duplicates into lists.
+  \item Normalization.
+After data is de-duplicated, the next step in data normalization is to establish foreign key
+relationships between children and parent entities and eliminate orphans: child records with
+non-existing parents.
+In ERNIE orphan records are deleted.
+An alternative normalization strategy could be to segregate orphans logically or physically while
+creating parent stub records.
+  \item Schema Permanence.
+In order to improve availability of data and simplify data schema management, ERNIE ETL scripts are
+designed to avoid recreating of main entities, for example, by using TRUNCATE TABLE instead of table re-creation.
+  \item Data Stewardship.
+ERNIE data stewards are people responsible for quality of a particular data subject area.
+Data stewards get notified when a data issue is detected and drive the workflows necessary for data
+issue remediation.
+They are also typically responsible for communicating changes in data structures.
+\end{itemize}
+
+\emph{Data mining and digitization} A set of source documents relevant to the question being asked is assembled and mined for citations to scientific literature using manual or semi-automated methods.
+Manual extraction involved searching for text strings that represent references of interest and matching those to unique identifiers in PubMed and/or Web of Science.
+As an example, the medical review document relevant to approval of ipilimumab contained X references.
+Y of them were matched to PubMed identifiers using the PubMed either through its web interface or the E-utils API.
+ERNIE is designed to support semi-automated case studies.
 
@@
 \section*{Results and Discussion}
-
 \section*{Acknowledgments} Research and development reported in this publication was supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract No.

### 2017-12-26 LaTeX/Paper2/paper2.tex
update

@@
 The first two case studies serve to validate ERNIE through reproducing the results of prior studies~\cite{Williams2015} on ivacaftor and ipilimumab, breakthrough drugs used to treat cystic fibrosis and melanoma.
-The remaining case studies concern drugs used to treat opioid addiction~\cite{Blumberg1973,Cowan1977} , a microarray system for pharmacogenomic profiling~\cite{deLeon2006}, a target discovery system originating from enzyme fragment complementation assays~\cite{Khanna1989}, and a behavioral intervention for substance abuse~\cite{Botvin1980}.
+The remaining case studies concern two drugs used to treat opioid addiction~\cite{Blumberg1973,Cowan1977} , a microarray system for pharmacogenomic profiling~\cite{deLeon2006}, a target discovery system originating from enzyme fragment complementation assays~\cite{Khanna1989}, and a behavioral intervention for substance abuse~\cite{Botvin1980}.
 The datasets that result from these studies are made available for use by other researchers and the workflows used to generate them are also archived to permit reproduction of our results, as well as review and modification of the methods used to generate them.
@@
 
-\emph{Open Source} All ERNIE code is open-source under the MIT license and available on GitHub ~\cite{GithubERNIE2017}.
-
-\emph{Infrastructure} ERNIE runs on two CentOS 7.4 Linux servers in the Microsoft Azure cloud with 10 terabytes of
-attached storage.
-One server, Azure standard D8s v3 (8 VCPUs, 32 Gb RAM), hosts data in a PostgreSQL 9.6 relational database, and
-additionally acts as a central hub for data related processes.
-A second server, an Azure standard DS4 (8 VCPUs, 28 Gb), runs Apache Solr 7.x search server, which is used to to create
-and store indexes of ERNIE data to facilitate fast free-text user searches.
-Access to ERNIE servers is secured through SSH tunneling and two-factor authentication, with a unique time-based code
-acting as one of the factors.
-
-Automated ERNIE processes are managed by the Jenkins Continuous Integration server.
-Custom Extract-Transform-Load (ETL) scripts are developed in Bash, Python, Java and SQL.
-Jenkins is additionally used to deploy scripts dedicated to data transformation and perform other
-calculations.
-In that regard, Jenkins is used to direct construction of Solr indexes as new data is introduced into
-ERNIE, as well as the construction of citation networks for specified topics.
-The Solr indexes can handle varying forms of Lucene-based search and full-text search, and may quickly return
-informative, ranked, and scored query results so that a user may be able to map data across sources.
-The citation networks are sub-networks (based largely in the Web of Science) that are generated based upon user input
-and subsequently analyzed.
+\emph{Infrastructure} ERNIE runs on two CentOS 7.4 Linux servers in the Microsoft Azure cloud with 10 terabytes of attached storage.
+One server, Azure standard D8s v3 (8 VCPUs, 32 Gb RAM), hosts data in a PostgreSQL 9.6 relational database, and additionally acts as a central hub for data related processes.
+A second server, an Azure standard DS4 (8 VCPUs, 28 Gb), runs Apache Solr 7.1 search server, which is used to to create and store indexes of ERNIE data to facilitate fast free-text user searches.
+Access to ERNIE servers is secured through SSH tunneling and two-factor authentication, with a unique time-based code acting as one of the factors.
 
@@
 Documentation is available on GitHub.
+Custom Extract-Transform-Load (ETL) scripts are developed in Bash, Python, Java and SQL.
+Automated processes are managed by the Jenkins Continuous Integration server, which is additionally used to deploy scripts dedicated to data transformation, direct construction of Solr indexes as new data is introduced into ERNIE, and build citation networks for case studies.
+Solr indexes can handle varying forms of Lucene-based search and full-text search, and quickly return informative, ranked, and scored query results so that a user may be able to map data across sources.
+The citation networks are sub-networks (based largely in the Web of Science) that are generated based upon user input and subsequently analyzed.
+All ERNIE code is shared as open-source under the MIT license and is available on GitHub ~\cite{GithubERNIE2017}.
 
-\emph{Data architecture and governance} ERNIE is aiming to provide data of best possible quality to
-its analysts and users.
-ERNIE data is extracted from several upstream sources of varying quality hence the need to cleanse
-data.
-ERNIE's approach to cleansing is to prefer data quality and normalized data over data completeness.
-The following are key aspects of ERNIE's data architecture and governance:
-\begin{itemize}
-  \item De-duplication.
-De-duplication is a process of eliminating logically duplicate records, that is records with
-identical primary or unique keys.
-In ERNIE duplicate records from such a group are deleted while leaving in place a single
-representative record (preferring a record which is updated last).
-An alternative de-duplication strategy could be to aggregate differing non-key fields from logical
-duplicates into lists.
-  \item Normalization.
-After data is de-duplicated, the next step in data normalization is to establish foreign key
-relationships between children and parent entities and eliminate orphans: child records with
-non-existing parents.
-In ERNIE orphan records are deleted.
-An alternative normalization strategy could be to segregate orphans logically or physically while
-creating parent stub records.
-  \item Schema Permanence.
-In order to improve availability of data and simplify data schema management, ERNIE ETL scripts are
-designed to avoid recreating of main entities, for example, by using TRUNCATE TABLE instead of table re-creation.
-  \item Data Stewardship.
-ERNIE data stewards are people responsible for quality of a particular data subject area.
-Data stewards get notified when a data issue is detected and drive the workflows necessary for data
-issue remediation.
+\emph{Data architecture and governance} ERNIE data is extracted from several upstream sources of varying quality and the  approach to cleansing is to prefer data quality and normalized data over data completeness.
+The following are key aspects of ERNIE's data architecture and governance.
+(i) De-duplication to eliminate logically duplicate records, that is records with identical primary or unique keys.
+In ERNIE duplicate records from such a group are deleted while leaving in place a single representative record (preferring a record which is updated last) (ii) Normalization to establish foreign key relationships between children and parent entities and eliminate orphans: child records with non-existing parents.
+)iii) Schema permanence to improve availability of data and simplify data schema management (iv) Data Stewardship to assign responsibility for quality of a particular data subject area.
+Data stewards are notified when a data issue is detected and drive the workflows necessary for data issue remediation.
 They are also typically responsible for communicating changes in data structures.
-\end{itemize}
-
-\emph{Data mining and digitization} A set of source documents relevant to the question being asked is assembled and mined for citations to scientific literature using manual or semi-automated methods.
-Manual extraction involved searching for text strings that represent references of interest and matching those to unique identifiers in PubMed and/or Web of Science.
-As an example, the medical review document relevant to approval of ipilimumab contained X references.
-Y of them were matched to PubMed identifiers using the PubMed either through its web interface or the E-utils API.
-ERNIE is designed to support semi-automated case studies.
 
@@
 
-\emph {Source document identification}
+\emph {Source document identification} A set of source documents relevant to the question being asked is assembled and mined for citations to scientific literature using manual or semi-automated methods.
 
-\emph {Citation extraction} Input and end product
+\emph {Citation extraction and matching} Manual extraction involves searching for text strings that represent references of interest and matching those to unique identifiers in PubMed and/or Web of Science.
+For example, the medical review document relevant to approval of ipilimumab contained X references.
+Y of them were matched to PubMed identifiers using the PubMed either through its web interface or the E-utils API.
+ERNIE is designed to support semi-automated case studies.
 
@@
 \section*{Results and Discussion}
+
+Fig. 1 -Architecture
+
+Table 1- List of Case Studies
+
+Table 2- seedset, cited references, grants, etc for all 7
+
+Table 3- NIH support- other support from WoS?
+
+Figure 1-
+
+What can we say about substance abuse and opioid addiction.
+
 \section*{Acknowledgments} Research and development reported in this publication was supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract No.

### 2017-12-29 Analysis/generic_network/generic_delim_generator.R
sql and R scripts for network analysis

@@ -1,0 +1,8 @@
+# Take a csv file and converts it into tab delimited
+
+print("this is a test",stdout())
+t <- read.csv("/tmp/genric_final.csv",stringsAsFactors=FALSE)
+library(caroline)
+write.delim(t,file="/tmp/generic_final_delim.txt",row.names=FALSE,sep="\t")
+
+

### 2017-12-29 Analysis/Network_Analyzer/EdgeNodeGeneretor.java
Network Analysis Application

@@ -1,9 +1,0 @@
-
-public class EdgeNodeGeneretor {
-
-	public static void main(String[] args) {
-		// TODO Auto-generated method stub
-
-	}
-
-}

### 2017-12-29 Analysis/Network_Analyzer/MASTER_DRIVER.sh

@@ -1,6 +1,24 @@
 
 
 
+#  Author: Samet Keserci
+#  Date: November 2017
+#  Usage: sh MASTER_DRIVER.sh <drug_name> <input_directory> <output_directory>
+#       Parameters:
+#       drug_name= mandatory parameters. It should be given as it appears in file name
+#       input_directory= The directory where the input files exist
+#       output_directory= The directory that output files will be located.
+
+#       For Example
+#       Input_directory  must contains following files  and formats for a given  drug_name="ivacaftor";
+#       ivacaftor_citation_network.txt
+#       ivacaftor_citation_network_authors.txt
+#       ivacaftor_citation_network_grants.txt
+#       ivacaftor_generational_references.txt
+
+
+
+
 
 if [ $# != 3 ]
 then

### 2017-12-29 Analysis/Network_Analyzer/Main.java

@@ -1,14 +1,0 @@
-
-public class Main {
-
-	
-	
-	
-	
-	
-	public static void main(String[] args) {
-		// TODO Auto-generated method stub
-
-	}
-
-}

### 2017-12-29 Analysis/Network_Analyzer/MainDriver.java

@@ -3,7 +3,7 @@
 
 	Author: Samet Keserci
 	Date: November 2017
-	Usage: sh run_network_analysis.sh <drug_name> [input_directory] [output_directory]
+	Usage: sh MASTER_DRIVER.sh <drug_name> [input_directory] [output_directory]
 		   Parameters:
 		   drug_name= mandatory parameters. It should be given as it appears in file name
 		   default input_directory="~/ERNIE/Analysis/" + drug_name + "/input/"

### 2017-12-29 Analysis/Network_Analyzer/PreProcess.java

@@ -1,15 +1,0 @@
-
-public class PreProcess {
-	
-	static String drug_name = "ivacaftor";
-	static String home = System.getProperty("user.home");
-	static String input_dir = home + "/ERNIE_CNI/" + drug_name + "/input/";
-	static String mid_dir = home + "/ERNIE_CNI/" + drug_name + "/mid_output/";
-	static String final_dir = home + "/ERNIE_CNI/" + drug_name + "/final_output";
-
-	public static void main(String[] args) {
-		
-		
-	}
-
-}

### 2017-12-29 Analysis/generic_network/NetworkAnalyzer.py

@@ -1,0 +1,485 @@
+
+
+
+
+'''
+Author      : Samet Keserci
+Create date : 12/25/2017
+Aim         : This script takes 5 columns data in the following format with a tab separated delimiter.
+               Columns:
+                   id: this is neccessary for pandas module. It must be numeric or integer, and must be the first columns.
+                   source: Contains the nodes
+                   stype: Type of the source nodes, such as wosid1, wosid1, wosid fda, ct, root etc.
+                   target: Contains target nodes
+                   ttype: Type of the targets as above.
+            As an output, it porduuces two csv file located in the output directory. Namely,
+                author_scores.csv: Has three columns; author, citaiton, PIR
+                publication_score: Has three columns; publication, citation, weighted_citation
+        
+Usage       : python NetworkAnalyzer.py -file_name <file name> -input_dir <input directory> -output_dir <output directory> 
+            where <file name> is just file name with its extension
+                  <input directory> is the directory where your input file is located.
+                  <output directory> is the directory where your output files will be located.
+'''
+
+
+
+
+
+import pandas as pd #use pandas to read the TSV file
+import sys #used to pass the TSV file
+import numpy as np
+#import imat_to_matrix as g_to_m
+#from scipy.sparse import csc_matrix
+from collections import defaultdict
+import csv
+
+
+
+
+'''
+Graph type input based Network Analysis
+'''
+
+
+def CorePubByPageRank(filename,top = 30):
+    
+    coreNodeList = CoreNodeList(filename)
+    page_rank = pageRank(filename,s=.85,maxiter=1)
+    
+    page_rank_sorted = sorted(pageRank(G,s=.8,maxerr=.001).items(), key=lambda x: x[1])
+    
+
+def CorePubByWeightCitation(filename,top = 30):
+    
+    coreNodeList = CoreNodeList(filename)
+    page_rank = pageRank(filename,s=.85,maxiter=10)
+    
+    
+
+def Weigted_Citation_G(filename):
+    
+    
+    G = EdgeListToMatrix(filename)
+
+    n = G.shape[0]
+    
+    node_list = NodeList(filename);
+    print node_list
+    weigted_citation = dict();
+    gamma = np.zeros(n);
+    
[…]

### 2017-12-29 Analysis/Network_Analyzer/AuthorScores.java
revision

@@ -10,8 +10,8 @@ public class AuthorScores {
 
 	MainDriver dirs = new MainDriver();
 
-	
-	
+
+
 	public static void test(){
 		System.out.println("TESET");
 	}
@@ -35,7 +35,7 @@ public class AuthorScores {
 			out.put(auth, sum);
 
 		}
-		
+
 		return out;
 	}
 
@@ -143,38 +143,38 @@ public class AuthorScores {
 			System.out.println(auth + "," + indeg + "," + indeg_scaled + "," + totCit + "," + totCit_scaled);
 
 		}
-		
-		
-		
-		
+
+
+
+
 
 		writer.close();
-		
+
 		//  call stat collector
 
 		System.out.println("stat collector is called: ");
 		mappers.wos_pmid_mapping_stat();
 
 	}
-	
-	// Make this tree set and run it from there. 
+
+	// Make this tree set and run it from there.
 	public  void final_stat_collector() throws IOException{
-		
+
 		TreeSet<String> dupChecker = new TreeSet<String>();
 		FileReader readstat = new FileReader(dirs.getFinalDir() + "stat_collector.txt");
-		BufferedReader statReader = new BufferedReader(readstat); 
-		
+		BufferedReader statReader = new BufferedReader(readstat);
+
 		FileWriter final_stat_collector = new FileWriter(dirs.getFinalDir() + "/final_stat_collector.txt");
-		
+
 		String stats = statReader.readLine();
 		while(stats !=null ){
-		
-			
+
+
 				dupChecker.add(stats);
-			
+
 				stats = statReader.readLine();
 		}
-		
+
 		int formatter = 0;
 		for (String s: dupChecker){
 			    if (++formatter%2 ==0) final_stat_collector.write("\n");
@@ -183,24 +183,24 @@ public class AuthorScores {
 		final_stat_collector.close();
 		statReader.close();
 		readstat.close();
-		
-		
+
+
 	}
 
 	public static void main(String[] args) throws IOException {
 
-		
+
 
 		AuthorScores authorscores = new AuthorScores();
 		 authorscores.auth_Scores("wos");
-		 
+
 
 		//System.out.println(authorscores.author_totalCitation("wos"));
-        
+
 		//test();
-		
-		
-		
+
+
+
 		// Mappers mappers = new Mappers();
 		// mappers.auth_pubSet_MAP("wos");
 

### 2018-01-06 LaTeX/Paper2/paper2.tex

@@
 \usepackage{listings}
+\usepackage{url}
 
@@
 
-Data mining of public and commercially available data sources coupled with network analysis has been successfully used as a digital methodology to study research collaborations and knowledge flow associated with drug development.
+Data mining coupled to network analysis has been successfully used as a digital methodology to study research collaborations and knowledge flow associated with drug development.
 To enable quantitative studies based on this approach, we have developed Enhanced Research Network Information Environment (ERNIE), a scalable cloud-based knowledge platform that integrates free data drawn from public sources as well as licensed data from commercially available ones.
 Analytical workflows in ERNIE are partially automated to enable expert input at critical stages.
-To facilitate adoption, reuse and extensibility, ERNIE was built with open source tools.
-and a modular design enables the facile addition, deletion, or substitution of data sources.
-To demonstrate the capabilities of ERNIE, we report the results of seven case studies that span drug development, pharmacogenomics, target discovery, behavioral interventions, and opioid addiction.
+To facilitate adoption, reuse and extensibility, ERNIE is built with open source tools.
+and a modular design enables facile addition, deletion, or substitution of data sources.
+To demonstrate the capabilities of ERNIE, we report the results of seven case studies that span opioid addiction, pharmacogenomics, target discovery, behavioral interventions, and drug development.
 In these studies, we mine and analyze data from policy documents, regulatory approvals, research grants, bibliographic and patent databases, and clinical trials, to document collaborations and identify influential research accomplishments.
-ERNIE is a template for repositories that can be used to support expert qualitative assessments, while offering burden reduction through automation and access to integrated data.
+ERNIE is presented as an accessible template for repositories that can be used to support expert qualitative assessments, while offering burden reduction through automation and access to integrated data.
 
@@
 The risk of research evaluation being driven by data and metrics with insufficient consideration of balanced judgment has driven the formulation of  sound principles to advise practice~\cite{LeidenManifesto2015}.
-However, data are still critical for evaluation, and utilitarian approaches for capture, integration, and archival that offer coverage and burden reduction assist the practice of research evaluation.
-While bibliographic data is usually central to research evaluation, the use of administrative records such as government statistics and research funding offers complementary value~\cite{FedStat2017}.
+Data are still critical for evaluation, however, and utilities for capture, integration, curation, archival, and analysis that offer coverage and burden reduction can only assist the practice of research evaluation.
+Bibliographic data, often central to research evaluation, with the complementary use of administrative records such as government statistics and research funding are of considerable value~\cite{FedStat2017}.
+In this regard, Williams and colleagues have conducted network analysis of mined data from publicly available administrative, regulatory, and scientific resources to define relationships between scientific discoveries and major advances in medicine such as new drugs~\cite{Williams2015}.
+Extending this citation-centric approach, we have documented the scientific collaborations that extend across networks underlying the development of five independently developed therapeutics for cancer~\cite{Keserci2017}.
+Analysis of such networks supports new insights into collaboration, knowledge diffusion, and recursive learning \textit{(vide supra)}.
 
-Using data mining of publicly available administrative, regulatory, and scientific records and network analysis, Williams and colleagues defined relationships between scientific discoveries and major advances in medicine such as new drugs~\cite{Williams2015}.
-Extending this work, we have previously documented the scientific collaborations that extend across networks underlying the development of five independently developed therapeutics for cancer~\cite{Keserci2017}.
-Analysis of such networks supports new insights into collaboration, knowledge diffusion, and recursive learning \textit{( videsupra)}.
-The framework we developed to mine data and integrate it into networks for analysis incorporates expert input, is flexible , can be further automated, adapted to a range of subjects beyond drug development, and used to support individual researchers, groups, and research organizations engaged in research assessment.
-In addition, cloud computing and data science have evolved to the point where scalable computing services and analytical methods are accessible to a broad user population.
-Thus, we have developed Enhanced Research Network Informatics Environment (ERNIE), a knowledge platform that integrates publicly available data as well as data from commercial sources.
-
-In demonstration that is focused on the theme of data mining and network analysis, we have used the data within ERNIE to conduct seven case studies.
+Cloud computing has also evolved to the point where scalable computing services and analytical methods can be made accessible to a broad user population and exerts a democratizing effect on research activities~\cite{Barga2011}.
+To take advantage of these advances in infrastructure and methodology, we have developed Enhanced Research Network Informatics Environment (ERNIE), a knowledge platform for research evaluation that integrates publicly available data as well as data from commercial sources.
+Focused on the theme of data mining and network analysis and to demonstrate the utility of ERNIE, we have used its data to conduct seven case studies.
 In these studies, we mine and analyze data from policy documents, regulatory approvals, research grants, bibliographic and patent databases, and clinical trials, to document collaborations and identify influential research accomplishments.
-The workflows used incorporate expert knowledge into defining a set of core documents from which citations can be extracted, linked to other records in ERNIE, and analyzed.
+The framework used to mine data and integrate it into networks for analysis incorporates expert input is simple, flexible, can be further automated, adapted to a range of subjects beyond drug development, and used to support individual researchers, groups, and research organizations engaged in research assessment.
+The workflows for these case studies incorporate expert knowledge into defining a set of core documents from which citations can be extracted, linked to other records in ERNIE, and analyzed.
 The first two case studies serve to validate ERNIE through reproducing the results of prior studies~\cite{Williams2015} on ivacaftor and ipilimumab, breakthrough drugs used to treat cystic fibrosis and melanoma.
-The remaining case studies concern two drugs used to treat opioid addiction~\cite{Blumberg1973,Cowan1977} , a microarray system for pharmacogenomic profiling~\cite{deLeon2006}, a target discovery system originating from enzyme fragment complementation assays~\cite{Khanna1989}, and a behavioral intervention for substance abuse~\cite{Botvin1980}.
+The remaining case studies relate to the current national crisis on substance abuse and concern two drugs used to treat opioid addiction~\cite{Blumberg1973, Cowan1977}, a microarray system for pharmacogenomic profiling~\cite{deLeon2006}, a target discovery system originating from enzyme fragment complementation assays that has been used in opioid receptor studies~\cite{Khanna1989}, and a behavioral intervention for substance abuse~\cite{Botvin1980}.
 The datasets that result from these studies are made available for use by other researchers and the workflows used to generate them are also archived to permit reproduction of our results, as well as review and modification of the methods used to generate them.
@@
 
-\emph{Infrastructure} ERNIE runs on two CentOS 7.4 Linux servers in the Microsoft Azure cloud with 10 terabytes of attached storage.
-One server, Azure standard D8s v3 (8 VCPUs, 32 Gb RAM), hosts data in a PostgreSQL 9.6 relational database, and additionally acts as a central hub for data related processes.
-A second server, an Azure standard DS4 (8 VCPUs, 28 Gb), runs Apache Solr 7.1 search server, which is used to to create and store indexes of ERNIE data to facilitate fast free-text user searches.
+\emph{Infrastructure} ERNIE runs on two IaaS CentOS 7.4 Linux servers in the Microsoft Azure cloud.
+One server, a standard D8s v3 (8 vCPUs, 32 Gb RAM) with 8 Tb of attached SSD storage, acts as a central hub for data related processes and hosts data in a PostgreSQL 9.6 relational database.
+The second server, a standard DS4 (8 vCPUs, 28 Gb) with 1 Tb of attached SSD storage also runs CentOS 7.4 and has the Apache Solr 7.1 search server installed.
+The design of ERNIE includes a PaaS Apache Spark cluster with 9 nodes  that is provisioned, using HDInsight, on demand and  is used for compute intensive tasks with Apache Sqoop, PySpark (Spark Python API), and data in Parquet format.
 Access to ERNIE servers is secured through SSH tunneling and two-factor authentication, with a unique time-based code acting as one of the factors.
+Interactive users have access to Python, SQL, R, Java, and standard Linux utilities.
+JupyterHub has also been installed to enable remote access to the Jupyter notebook server for multiple users.
 
-\emph{Data sources} Data in ERNIE are extracted from both publicly available and commercial sources.
-Publicly available data are copied from the National Clinical Trials Database \cite,  the FDA Orange and Purple Books \cite, the United States Patent Office \cite, and NIH ExPORTER \cite.
-Leased data are acquired from Clarivate Analytics and consist of the Web of Science Core Collection and the Derwent World Patent Index~\cite{DWPI2017}.
-The data in ERNIE are stored in a relational schema that is documented.
-Documentation is available on GitHub.
-Custom Extract-Transform-Load (ETL) scripts are developed in Bash, Python, Java and SQL.
-Automated processes are managed by the Jenkins Continuous Integration server, which is additionally used to deploy scripts dedicated to data transformation, direct construction of Solr indexes as new data is introduced into ERNIE, and build citation networks for case studies.
-Solr indexes can handle varying forms of Lucene-based search and full-text search, and quickly return informative, ranked, and scored query results so that a user may be able to map data across sources.
-The citation networks are sub-networks (based largely in the Web of Science) that are generated based upon user input and subsequently analyzed.
-All ERNIE code is shared as open-source under the MIT license and is available on GitHub ~\cite{GithubERNIE2017}.
+\begin{figure}[!h]
+%\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\centering
+\scalebox{0.99}
+{
+\begin{subfigure}{.5\textwidth}
+  \centering
+\includegraphics[width=.95\linewidth]{ERNIE_System_Context_2.pdf}
+  \label{fig:sub1}
+\end{subfigure}
+\begin{subfigure}{.5\textwidth}
+  \centering
+ \includegraphics[width=.95\linewidth]{ERNIE_System_Context_1.pdf}
+  \label{fig:sub2}
+\end{subfigure}
+}
+\caption{{\bf System Context View} ERNIE runs on two IaaS CentOS 7.4 Linux servers in the Microsoft Azure cloud.
+\emph{Left Panel.} Users interactively access the environment through multifactor authentication (MFA).
+\emph{Right Panel.} ERNIE data is populated through automated custom ETL processes }
+\label{fig: test}
+%\end{adjustwidth}
+\end{figure}
 
-\emph{Data architecture and governance} ERNIE data is extracted from several upstream sources of varying quality and the  approach to cleansing is to prefer data quality and normalized data over data completeness.
-The following are key aspects of ERNIE's data architecture and governance.
-(i) De-duplication to eliminate logically duplicate records, that is records with identical primary or unique keys.
+\emph{Data sources} Data in ERNIE are derived from both publicly available and commercial sources and are stored in a documented relational schema.
+Publicly available data are copied from ClinicalTrials.gov~\cite{ClinicalTrials2017},  the US Food and Drug Administration (FDA) Orange~\cite{OrangeBook2017} and Purple~\cite{PurpleBook2017} Books, the United States Patent Office~\cite{USPTO2017}, and NIH ExPORTER~\cite{NIHExporter2017}.
+Leased data are acquired from Clarivate Analytics and consist of the Web of Science Core Collection~\cite{WoS2017} and the Derwent World Patent Index~\cite{DWPI2017}.
+Web of Science, Patents, Clinical Trials, and Clinical Guidelines data are updated weekly.
+All other data sources are updated monthly.
+Custom Extract-Transform-Load (ETL) scripts developed in Bash, Python, Java and SQL are used for initial loading as well as refreshes.
+Automated processes are managed by the Jenkins Continuous Integration server, which is used to (i) deploy scripts dedicated to data transformation (ii) direct construction of Solr indexes as new data is introduced into ERNIE (iii) build citation networks for case studies (iv) manage data refreses.
+All ERNIE code is shared as open-source under the MIT license and is available on GitHub~\cite{GithubERNIE2017}.
+Table 1 provides an overview of the total count of records in major data sources (excluding records from tables used to process data) in the schema in ERNIE.
+% latex table generated in R 3.4.3 by xtable 1.8-2 package
+% Wed Jan  3 15:03:57 2018
+
+\begin{table}[ht]
+%\centering
+\begin{tabular}{rll}
+  \hline
+ & Data Source & No of Records \\ 
+  \hline
+1 & Web Of Science Core Collection & 2.5 x$10^{9}$\\ 
+  2 & Derwent US Patents & 2.4 x$10^{8}$\\
+  3 & NIH ExPORTER & 7.1 x$10^{6}$ \\ 
+  4 & NLM Clinical Trials & 8.6 x$10^{6}$ \\ 
+  5 &  FDA & 5.0 x$10^{4}$\\  
+  6 & AHRQ Clinical Guidelines & 2.6 x$10^{3}$ \\ 
+   \hline
+\end{tabular}
+\caption {Summed counts of records in ERNIE grouped by major data sources}
+\end{table}
+
+\emph{Data architecture and governance.} ERNIE data is drawn from several upstream sources of varying quality.
+Cleansing approaches in place are designed to favor data quality and normalized data over completeness.
+Key aspects of ERNIE's data architecture and governance are (i) De-duplication to eliminate logically duplicate records, that is records with identical primary or unique keys.
 In ERNIE duplicate records from such a group are deleted while leaving in place a single representative record (preferring a record which is updated last) (ii) Normalization to establish foreign key relationships between children and parent entities and eliminate orphans: child records with non-existing parents.
-)iii) Schema permanence to improve availability of data and simplify data schema management (iv) Data Stewardship to assign responsibility for quality of a particular data subject area.
+(iii) Schema permanence to improve availability of data and simplify data schema management (iv) Data Stewardship to assign responsibility for quality of a particular data subject area.
 Data stewards are notified when a data issue is detected and drive the workflows necessary for data issue remediation.
@@
 
-\emph{Workflows} The core workflow in ERNIE consists of (i) Source document identification, in which a set of source documents relevant to the question being asked is assembled  (ii) Citation extraction, in which text references to scientific publications and patents are matched to unique identifiers such as PubMed ID, UT (Web of Science Accession Number), or US patent number.
-(iii) Amplification, in which publications and patents linked by citation to extracted references are identified through citation records in the Web of Science (iv) Network analysis, in which the data assembled through the preceding stages are represented as a network and influential nodes are identified (v) Visualization of the network data to provide insight and stimulate further investigation.
+\emph{Workflows.} The core workflow in ERNIE can be divided into five stages (i) Source document identification, in which a set of source documents relevant to the question being asked is assembled  (ii) Citation extraction, in which text references to scientific publications and patents are matched to unique identifiers such as PubMed ID, UT (Web of Science Accession Number), or US patent number (iii) Amplification and linking, in which publications and patents linked by citation to extracted references are identified through citation records in the Web of Science and linked to other records in ERNIE (iv) Network analysis, in which the data assembled through the preceding stages are represented as a network and influential nodes are identified (v) Visualization of the network data to provide insight and stimulate further investigation.
 
-\emph {Source document identification} A set of source documents relevant to the question being asked is assembled and mined for citations to scientific literature using manual or semi-automated methods.
+\emph {Source document identification.} A set of source documents relevant to the question being asked is assembled and searched for citations to scientific literature.
+The process involves input from knowledgeable persons, is subjective, and centers around regulatory documents made available by the FDA, documents on government web sites such as the office of The Surgeon General, the White House, and the Office of National Drug Control Policy, and technical documents on corporate web sites such as those of DiscoverX and Affymetrix.
+For example, the The Surgeon General's Report on Alcohol, Health, and Addiction~\cite{SurgGen2017} and The President's Commission on Combating Drug Addiction and The Opioid Crisis~\cite{PresidComm2017} were identified as key source documents relevant to the Life Skills Training Case study in this article.
 
-\emph {Citation extraction and matching} Manual extraction involves searching for text strings that represent references of interest and matching those to unique identifiers in PubMed and/or Web of Science.
-For example, the medical review document relevant to approval of ipilimumab contained X references.
-Y of them were matched to PubMed identifiers using the PubMed either through its web interface or the E-utils API.
-ERNIE is designed to support semi-automated case studies.
+\emph {Citation extraction and matching.} References to scientific literature and patents found in the source documents are matched to unique identifiers using manual or partially-automated in the Web of Science Core Collection~\cite{Keserci2017}.
+Manual extraction involves searching for text strings that represent references of interest and matching those to unique identifiers in PubMed and/or Web of Science.
+For example, US6984720 B1, the core patent relevant to ipilimumab contained 52 references to scientific publications listed under non-patent citations.
+All 52 of them were manually matched to PubMed identifiers (pmid) using the PubMed website.
+In a second approach, a partially-automated one, Apache Solr is used to to create and store indexes of ERNIE data that can facilitate user searches that return informative, ranked, and scored query results and form the basis for a semi-automated process that takes advantage of indexed Web of Science publications in ERNIE.
+In this process, a text file containing references is passed as input to a Python script and a user manually selects from the output hit list that includes citation information, a Web of Science Accession Number (UT), and the numeric output of the Solr scoring function.
+The latter process offers scalability and can process 30-40 references per minute.
+A combination of these approaches was used in the seven case studies described.
+The product of citation extraction and matching is termed the seedset.
 
-\emph {Amplification} What is the input and end product
+\emph{Amplification.} Once unique identifiers to scientific literature are assembled in the seedset, cited and/or citing references in the Web of Science Core Collection are identified using the wos\_references table (see schema).
+Only those records with an entry in the wos\_publications table (see schema) are considered when counting citing or cited references.
+These are then linked to authors using Web of Science data.
+Wherever possible, UTs are mapped to pmids using a lookup table and then to grants using data linking publications to grant support from NIH ExPORTER.
 
-\emph{Network analysis} Input and end product
+\emph{Network analysis.} For network  analysis, 4 input files are used that are derived from the amplification stage (i) Article and Author edge list, a mapping of publications to authors.
+(ii) Article and first generation citations, a list of seedset and a single generation of cited or citing references derived from the amplification cycle.
+(iii) Publication and publication edge list, the citation network after amplification stored as source-target citation pairs.
+(iv) Publication and published year: A mapping of publications to their year of publication.
+Once these four files are generated, the network analyzer code generates 7 output files:
+
+\begin{enumerate}
+  \item Author scores based on PubMed and WoS. These are mappings of publications to their authors using either PubMed or Web of Science data. 
+  \item Article scores based on PubMed and WoS: These one  contains the information of seed set and its first generation without inter citation information.
+  \item Edge List of Articles for Visualization based on PubMed and WoS. These is the citation network of the publications after amplification.
+  \item Descriptive statistics: This file contains  basic descriptive statistics about articles and authors such as counts, max citations, and number of lost nodes during the various mapping. 
+\end{enumerate}
+
+Sample metrics for Authors are number of articles, total citation and propagated in-degree rank (PIR) ~\cite{Williams2015}, and for articles we calculate the in network citation, weighted citation (propagated citation with depth = 2).
+In Each case study,  we calculate the scores as below:
+
+Given the articles-to-articles citation relation, let matrix $G$ be a $n$x$n$ matrix where $n$ represent the number of articles in the network be a Matrix representation of the Network. We define 
+the components $g_{ij}$ of the matrix $G$ as follows,
+
+\begin{equation*}
+g_{ij} = \begin{cases}
+1 &\text{$i^{th}$ articles cites $j^{th}$ article}\\
+0 &\text{Otherwise}
+\end{cases}
+\end{equation*}
+
+Then score of of an article  $\mathfrak{p}$ is denoted as $s(\mathfrak{p})$ and is represented by,
+
+\begin{equation*}
+s(\mathfrak{p}) = [u*G]_{j} = \sum_k^n  u_k \cdot g_{jk}
+\end{equation*}
+
+where $u$ is a weight vector. Here, for different weight vector, we will get different measurements.
+For example, for  $u=<1,1,1...,1>$,
+\begin{equation*}
+s(\mathfrak{p}_j) = [u*G]_{j} = \sum_k^n  u_k \cdot g_{jk}=\sum_k^n  1\cdot g_{jk}
+\end{equation*}
+which is just citation of the article $\mathfrak{p}_j$, denoted by $cit(\mathfrak{p}_j)$.
+There are various weight vector we could use such as weight based on the publication year, weight based on over all citation flow (~ Page rank), or we could have have normalized weight vector by it is average citation score.
+In these case studies we used one more weight vector to produce William et.all result.
+This new weight enable us not to count the number of citing papers, but also consider the citation based quality of citing papers.
+Considering the weight vector to be $u=<cit(\mathfrak{p}_1),cit(\mathfrak{p}_2),...,cit(\mathfrak{p}_n)>$, then weighted citation of a papers according to this weight vector will be
+
+\begin{equation*}
+s(\mathfrak{p}_j) = [u*G]_{j} = \sum_k^n  u_k \cdot g_{jk}=\sum_k^n  cit(g_k)\cdot g_{jk} =\sum_k^n  \{\sum_m^n  g_{km}\} \cdot g_{jk}
+\end{equation*}
+which could be translated as the total sum of citation of all citing papers. Next if we add self citation to above quantity we will get Pico type article scoring metric. i.e
+
+ \begin{equation}
+ \begin{split}
+s(\mathfrak{p}_j)+cit(\mathfrak{p}_j) & = \sum_k^n   \{\sum_m^n  g_{km}\} \cdot g_{jk} +cit(\mathfrak{p}_j)  \\
+						       & =\sum_k^n   \{\sum_m^n  g_{km}\} \cdot g_{jk}+ \sum_k^n  g_{jk} \\
+                                                          & =\sum_k^n   \{ 1+ \sum_m^n  g_{km} \} \cdot g_{jk}
+\end{split}                                                          
+\end{equation}
+
+As is seen above if we refine the weight vector to be as, 
+\begin{equation}\label{wu}
+u = < 1+ \sum_m^n  g_{1m}  ,  1+  \sum_m^n  g_{2m} , ...,  1 +  \sum_m^n  g_{nm} >
+\end{equation}
+then  we will get article scores method developed in Williams et.all.
+Similary we could use weight vector based on h-index, e-index of authors, normalized citation count, sum of a h-index of the authors etc.
+We leave choice of metrics to users.
+
+Next we calculate the scores of an authors $\mathfrak{a}$ as follows. Let matrix $\mathcal {A}$ be represent the Author publications relationship  by the following definition.
+
+\begin{equation}
+a_{ij} = \begin{cases}
+1 &\text{$i^{th}$ Author wrotes $j^{th}$ article}\\
+0 &\text{Otherwise}
+\end{cases}
+\end{equation}
+
+Then the score of the author $\mathfrak{a}_j$ will be defined as 
+\begin{equation}
+S(\mathfrak{a}_j) =  \sum_k^n a_{jk} \cdot  s(p_k) 
+\end{equation}
+
+where $s(p_k)$ denote the publication score for any given weight $u$.
+Here if we choose weight $u$ to be $ <1,1,1,,,,1>$ then resulting score will be just total citation count of the Author $\mathfrak{a}$ in the network.
+Whereas choosing weight function as in ( \ref{wu} ) gives the PIR score  of an author.
 
@@
 
-Table 1- List of Case Studies
+Table 2- List of Case Studies
 

### 2018-01-11 ExPORTER/Automation/exporter_update_auto.sh
Exporter updates

@@ -1,4 +1,4 @@
-#RePORTER Project weekly updates
+#EXPORTER Project weekly updates
 
 # Author: VJ Davey
 # Date: 12/08/17
@@ -17,10 +17,11 @@ if [ $? -ne 0 ]; then
   echo "Please perform a manual check of the Exporter website and manually update counter file if necessary"
   exit 1;
 fi
+wget -q "https://exporter.nih.gov/CSVs/final/RePORTER_PRJABS_C_FY${year}_$(printf "%03d" $week).zip" --no-check-certificate
 unzip $c_dir/*.zip; rm $c_dir/*.zip
 
 # pass the download to the python script to extract the proper columns, then copy the data into the temp table
-file=$(ls *.csv)
+file=$(ls RePORTER_PRJ_C*.csv)
 python $c_dir/column_extractor.py $file; file_extract=$(echo $file | sed s/.csv/_EXTRACTED.csv/g); file_extract=${c_dir}"/"${file_extract}
 # truncate the temp project table: temp_exporter_projects. Then update the table with data from the extract
 psql ernie -c "TRUNCATE TABLE temp_exporter_projects;"
@@ -28,6 +29,14 @@ psql ernie -c "COPY temp_exporter_projects from '${file_extract}' delimiter ',' 
 # merge the temp table into the main table, update old records with new records based on pk match
 # insert on conflict update
[…]

### 2018-01-11 ExPORTER/Smokeload/reporter_smokeload.sh

@@ -3,9 +3,10 @@
 # Date 09/26/2017
 
 link_files=$1
-proj_files=$2
-cur_dir=$3
-work_dir=$4
+projabs_files=$2
+proj_files=$3
+cur_dir=$4
+work_dir=$5
 echo 'STARTED'; date
 #create tables
 psql ernie -f create_reporter_tables.sql
@@ -13,14 +14,19 @@ psql ernie -f create_reporter_tables.sql
 cd $work_dir; for file in $(ls $link_files/*.zip); do unzip $file; done
 for file in $(ls $work_dir*.csv);do
   echo 'Working on file' $file
-  psql ernie -c "copy reporter_publink from '$file' delimiter ',' CSV HEADER;" ; wait ;
+  psql ernie -c "copy exporter_publink from '$file' delimiter ',' CSV HEADER;" ; wait ;
+done; rm $work_dir*.csv
+#unzip projabs_files, convert, and push into database
+cd $work_dir; for file in $(ls $projabs_files/*.zip); do unzip $file; done
+for file in $(ls $work_dir*.csv);do
+  echo 'Working on file' $file
+  psql ernie -c "copy exporter_project_abstracts from '$file' delimiter ',' CSV HEADER encoding 'latin1';" ; wait ;
 done; rm $work_dir*.csv
 #unzip proj_files, convert, and push into database
 cd $work_dir; for file in $(ls $proj_files/*.zip); do unzip $file; done
 for file in $(ls $work_dir*.csv);do
   echo 'Working on file' $file
   python $cur_dir/column_extractor.py $file; file_extract=$(echo $file | sed s/.csv/_EXTRACTED.csv/g)
-  psql ernie -c "copy reporter_projects from '$file_extract' delimiter ',' CSV HEADER;" ; wait ;
+  psql ernie -c "copy exporter_projects from '$file_extract' delimiter ',' CSV HEADER;" ; wait ;
 done; rm $work_dir*.csv
 echo 'FINISHED'; date
-

### 2018-01-11 Solr/mass_solr_search.py

@@ -49,7 +49,6 @@ queries=[]
 if search_file!=None:
     with open(search_file) as f:
         queries = f.read().splitlines()
-        print queries
 else:
     queries.append(query)
 

### 2018-01-11 LaTeX/Paper2/paper2.tex

@@
 To enable quantitative studies based on this approach, we have developed Enhanced Research Network Information Environment (ERNIE), a scalable cloud-based knowledge platform that integrates free data drawn from public sources as well as licensed data from commercially available ones.
-Analytical workflows in ERNIE are partially automated to enable expert input at critical stages.
 To facilitate adoption, reuse and extensibility, ERNIE is built with open source tools.
 and a modular design enables facile addition, deletion, or substitution of data sources.
+Additionally, analytical workflows in ERNIE are partially automated to enable expert input at critical stages.
 To demonstrate the capabilities of ERNIE, we report the results of seven case studies that span opioid addiction, pharmacogenomics, target discovery, behavioral interventions, and drug development.
@@
 The risk of research evaluation being driven by data and metrics with insufficient consideration of balanced judgment has driven the formulation of  sound principles to advise practice~\cite{LeidenManifesto2015}.
-Data are still critical for evaluation, however, and utilities for capture, integration, curation, archival, and analysis that offer coverage and burden reduction can only assist the practice of research evaluation.
-Bibliographic data, often central to research evaluation, with the complementary use of administrative records such as government statistics and research funding are of considerable value~\cite{FedStat2017}.
-In this regard, Williams and colleagues have conducted network analysis of mined data from publicly available administrative, regulatory, and scientific resources to define relationships between scientific discoveries and major advances in medicine such as new drugs~\cite{Williams2015}.
-Extending this citation-centric approach, we have documented the scientific collaborations that extend across networks underlying the development of five independently developed therapeutics for cancer~\cite{Keserci2017}.
+Supporting data for expert qualitative evaluation are still critical, however, and utilities for capture, integration, curation, and analysis that offer coverage and burden reduction will assist the practice of research evaluation.
+
+Bibliographic data are usually central to research evaluation, and their value is complemented by the use of administrative records such as government statistics and research funding~\cite{FedStat2017}.
+Relevantly, Williams and colleagues have conducted network analysis of mined data from publicly available administrative, regulatory, and scientific resources to define relationships between scientific discoveries and major advances in medicine, such as new drugs~\cite{Williams2015}.
+Extending this citation-centric approach, we have previously documented the scientific collaborations that extend across networks underlying the development of five independently developed therapeutics for cancer~\cite{Keserci2017}.
 Analysis of such networks supports new insights into collaboration, knowledge diffusion, and recursive learning \textit{(vide supra)}.
 
-Cloud computing has also evolved to the point where scalable computing services and analytical methods can be made accessible to a broad user population and exerts a democratizing effect on research activities~\cite{Barga2011}.
-To take advantage of these advances in infrastructure and methodology, we have developed Enhanced Research Network Informatics Environment (ERNIE), a knowledge platform for research evaluation that integrates publicly available data as well as data from commercial sources.
-Focused on the theme of data mining and network analysis and to demonstrate the utility of ERNIE, we have used its data to conduct seven case studies.
+As the scale of analysis increases, more robust computing resources become useful and sometimes necessary.
+Cloud computing has evolved to the point where scalable computing services and analytical methods are now available to a broad user population, and this availability exerts a democratizing effect on research activities~\cite{Barga2011}.
+
+To take advantage of these advances in methodology and infrastructure, we have developed Enhanced Research Network Informatics Environment (ERNIE), a knowledge platform for research evaluation.
+ERNIE integrates publicly available data as well as data from commercial sources and the framework that is used to mine data and integrate it into networks for analysis is simple and flexible.
+The datasets that result from analysis can be made available for use by other researchers, and the workflows used to generate them are also archived to permit  review, and reproduction.
+
+We demonstrate the utility of ERNIE in seven case studies.
 In these studies, we mine and analyze data from policy documents, regulatory approvals, research grants, bibliographic and patent databases, and clinical trials, to document collaborations and identify influential research accomplishments.
-The framework used to mine data and integrate it into networks for analysis incorporates expert input is simple, flexible, can be further automated, adapted to a range of subjects beyond drug development, and used to support individual researchers, groups, and research organizations engaged in research assessment.
-The workflows for these case studies incorporate expert knowledge into defining a set of core documents from which citations can be extracted, linked to other records in ERNIE, and analyzed.
-The first two case studies serve to validate ERNIE through reproducing the results of prior studies~\cite{Williams2015} on ivacaftor and ipilimumab, breakthrough drugs used to treat cystic fibrosis and melanoma.
+The workflows for these case studies incorporate subject matter knowledge into defining a set of core documents from which citations can be extracted, linked to other records in ERNIE, and analyzed.
+The first two case studies serve to validate ERNIE through reproducing the results of prior studies on ivacaftor and ipilimumab~\cite{Williams2015}, breakthrough drugs used to treat cystic fibrosis and melanoma.
 The remaining case studies relate to the current national crisis on substance abuse and concern two drugs used to treat opioid addiction~\cite{Blumberg1973, Cowan1977}, a microarray system for pharmacogenomic profiling~\cite{deLeon2006}, a target discovery system originating from enzyme fragment complementation assays that has been used in opioid receptor studies~\cite{Khanna1989}, and a behavioral intervention for substance abuse~\cite{Botvin1980}.
-The datasets that result from these studies are made available for use by other researchers and the workflows used to generate them are also archived to permit reproduction of our results, as well as review and modification of the methods used to generate them.
+
+ERNIE is presented as a simple extensible model for repositories that can be used to support expert qualitative assessments.
+Such repositories enable subject matter input into research evaluation while offering access to integrated data and burden reduction through automation.
+.
 
@@
 Access to ERNIE servers is secured through SSH tunneling and two-factor authentication, with a unique time-based code acting as one of the factors.
-Interactive users have access to Python, SQL, R, Java, and standard Linux utilities.
-JupyterHub has also been installed to enable remote access to the Jupyter notebook server for multiple users.
+Interactive users have access to Python and Jupyter notebook, SQL, R, Java, and standard Linux utilities.
 
@@
 %\begin{adjustwidth}{-0.5in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\centering
+%\centering
+\flushleft
 \scalebox{0.99}
@@
   \centering
-\includegraphics[width=.95\linewidth]{ERNIE_System_Context_2.pdf}
+\includegraphics[width=.95\linewidth]{ERNIE_System_Context_1.pdf}
   \label{fig:sub1}
@@
 \begin{subfigure}{.5\textwidth}
-  \centering
- \includegraphics[width=.95\linewidth]{ERNIE_System_Context_1.pdf}
+ % \centering
+ \includegraphics[width=.95\linewidth]{ERNIE_System_Context_2.pdf}
   \label{fig:sub2}
@@
 \caption{{\bf System Context View} ERNIE runs on two IaaS CentOS 7.4 Linux servers in the Microsoft Azure cloud.
-\emph{Left Panel.} Users interactively access the environment through multifactor authentication (MFA).
-\emph{Right Panel.} ERNIE data is populated through automated custom ETL processes }
+An Apache Spark cluster is provisioned on a PaaS basis for compute intensive tasks.
+\emph{Left Panel.} Users access the environment through multifactor authentication (MFA) and access the data server \emph{Right Panel.} ERNIE data is populated through automated custom ETL processes indexed by the Solr server for fast searches.}
 \label{fig: test}
@@
 Wherever possible, UTs are mapped to pmids using a lookup table and then to grants using data linking publications to grant support from NIH ExPORTER.
+As we have previously noted~\cite{Keserci2017}, the use of pmids for network construction results in significant loss of information since the intersection of bibliographic records between PubMed and Web of Science is relatively small.
 
@@
 (iii) Publication and publication edge list, the citation network after amplification stored as source-target citation pairs.
-(iv) Publication and published year: A mapping of publications to their year of publication.
-Once these four files are generated, the network analyzer code generates 7 output files:
+(iv) Publication and published year, a mapping of publications to their year of publication.
+Once these four files are generated, the network analyzer code generates 3 output files (i) Article scores based on weighted citation counts from within the network.
+(ii) A list of author scores based on article scores.
+(iii) Edge list of articles for Visualization.
+(iv) Descriptive statistics, this file contains descriptive statistics about articles and authors generated during network analysis.
+These output files are generated using both pmid-based or UT-based data, thus, [need to clarify].
 
-\begin{enumerate}
-  \item Author scores based on PubMed and WoS. These are mappings of publications to their authors using either PubMed or Web of Science data. 
-  \item Article scores based on PubMed and WoS: These one  contains the information of seed set and its first generation without inter citation information.
-  \item Edge List of Articles for Visualization based on PubMed and WoS. These is the citation network of the publications after amplification.
-  \item Descriptive statistics: This file contains  basic descriptive statistics about articles and authors such as counts, max citations, and number of lost nodes during the various mapping. 
-\end{enumerate}
+For each article, we calculate in-network citations, as well as weighted citations (sum of article citations plus sum of citations of an article's first degree neighbors).
+For each author, we calculate the number of articles, total citations and propagated in-degree rank (PIR) ~\cite{Williams2015}.
 
-Sample metrics for Authors are number of articles, total citation and propagated in-degree rank (PIR) ~\cite{Williams2015}, and for articles we calculate the in network citation, weighted citation (propagated citation with depth = 2).
-In Each case study,  we calculate the scores as below:
-
-Given the articles-to-articles citation relation, let matrix $G$ be a $n$x$n$ matrix where $n$ represent the number of articles in the network be a Matrix representation of the Network. We define 
+Given the article-to-article relation, let matrix $G$ be a $n$x$n$ matrix where $n$ represents the number of articles in the network. We define 
 the components $g_{ij}$ of the matrix $G$ as follows,
@@
 \end{equation*}
-which is just citation of the article $\mathfrak{p}_j$, denoted by $cit(\mathfrak{p}_j)$.
+which is citations of the article $\mathfrak{p}_j$, denoted by $cit(\mathfrak{p}_j)$.
 There are various weight vector we could use such as weight based on the publication year, weight based on over all citation flow (~ Page rank), or we could have have normalized weight vector by it is average citation score.

### 2018-01-11 Solr/solr_search.py
Solr Search update

@@ -1,0 +1,81 @@
+# This is an updated generalized script to search a core on a SOLR server for matches based on several search criteria
+# Usage:
+#        python mass_solr_search.py -c 'core_name' -qf 'query_field' -q|-f 'query or file' -ip 'solr ip address and port' -n 'number of solr results' -o 'output file name'
+# Example 1:
+#        python mass_solr_search.py -c wos_pub_core -qf citation -q "DNA microarray" -ip 10.0.0.5:8983 -n 10 -o dna_microarray.csv
+# Example 2:
+#        python mass_solr_search.py -c wos_pub_core -qf citation -f pirrung.txt -ip 10.0.0.5:8983 -n 5 -o pirrung.csv
+# Author: VJ Davey
+
+
+
+
+import sys; import string; import re ; import subprocess
+
+# Collect user input
+query=None; core=None; query_fields=[]; search_file=None; num_results=10; ip_and_port='localhost:8983' ; psql_ip='localhost' ; psql_port='5432'; output_file='temp.csv'
+for i in range(0,len(sys.argv)):
+    if sys.argv[i][0] == '-':
+        option = sys.argv[i]
+        if option[1:] in ['ip_and_port', 'ip']:
+            ip_and_port= sys.argv[i+1]
+        elif option[1:] in ['core', 'c']:
+            core = sys.argv[i+1]
+        elif option[1:] in ['query_field', 'qf']:
+            query_fields.append(sys.argv[i+1])
+        elif option[1:] in ['query', 'q']:
+            query = sys.argv[i+1] ;
+            if search_file!=None:
+                raise NameError('Choose either to use a query or a file. Not both and not neither.')
+        elif option[1:] in ['file', 'f']:
+            search_file = sys.argv[i+1] ;
+            if query!=None:
+                raise NameError('Choose either to use a query or a file. Not both and not neither.')
+        elif option[1:] in ['num_results', 'n']:
+            num_results = sys.argv[i+1]
+        elif option[1:] in ['output_file', 'o']:
+            output_file = sys.argv[i+1]
+        elif option[1:] in ['psql_ip', 'pi']:
+            psql_ip = sys.argv[i+1]
+        elif option[1:] in ['psql_port', 'pp']:
+            psql_port = sys.argv[i+1]
+        else:
+            raise NameError('Unknown option : \'%s\''%(option))
+if (core==None): raise NameError('Missing critical information - core')
+
+
[…]

### 2018-01-12 Solr/solr_search.py
solr updates

@@ -13,7 +13,7 @@
 import sys; import string; import re ; import subprocess
 
 # Collect user input
-query=None; core=None; query_fields=[]; search_file=None; num_results=10; ip_and_port='localhost:8983' ; psql_ip='localhost' ; psql_port='5432'; output_file='temp.csv'
+query=None; core=None; query_fields=[]; target_fields=[]; search_file=None; num_results=10; ip_and_port='localhost:8983' ; psql_ip='localhost' ; psql_port='5432'; output_file='temp.csv'
 for i in range(0,len(sys.argv)):
     if sys.argv[i][0] == '-':
         option = sys.argv[i]
@@ -23,6 +23,8 @@ for i in range(0,len(sys.argv)):
             core = sys.argv[i+1]
         elif option[1:] in ['query_field', 'qf']:
             query_fields.append(sys.argv[i+1])
+        elif option[1:] in ['target_field', 'tf']:
+            target_fields.append(sys.argv[i+1])
         elif option[1:] in ['query', 'q']:
             query = sys.argv[i+1] ;
             if search_file!=None:
@@ -47,9 +49,10 @@ if (core==None): raise NameError('Missing critical information - core')
 # Set up for the queries. If the user has not specified any fields for the query, check the core for all fields, return a comma seperated list, and use those returned fields for the dismax query
 field_collector_string="curl \'http://%s/solr/%s/select?&q=\"*:*\"&wt=csv&rows=0\'"%(ip_and_port, core)
 fields=subprocess.check_output(field_collector_string, shell=True).rstrip().split(","); fields.remove('id') ; fields=fields if len(query_fields) < 1 else query_fields
+fields=[i for i in fields if i not in target_fields]
 #TODO: In future, make sure this is adjustable for weight
 field_list_string1='%20'.join(fields)
-field_list_string2=','.join(['id','score']+fields)
+field_list_string2=','.join(['id','score']+target_fields+fields)
 curl_search_string="curl \'http://%s/solr/%s/select?defType=dismax&qf=%s&fl=%s&q=:"%(ip_and_port, core, field_list_string1,field_list_string2)
 curl_search_string_ending='&rows=%s&wt=csv&csv.separator=~\''%(num_results)
 
@@ -66,7 +69,7 @@ else:
 
 # The actual run. Return results on the query. Hardcode any mapping to other DB information as needed if dealing with something like a WOS to PMID mapping
[…]

### 2018-01-13 Guidelines/Automation/cg_update_auto.sh
#ER-71 Transition to Permanent Database Objects * CG WIP

@@ -1,50 +1,60 @@
-#!/bin/sh
-
-# This script updates Clinical Guidelines (CG) tables cg_*.
-# Specifically:
-# 1. Download a complete list of CG from website;
-# 2. Get the links with CG uids.
-# 3. Use Python to scrape the links to get PMIDs if there's any.
-# 4. Update uids and PMIDs to cg tables cg_*.
-
-# Tables updated: cg_uids, cg_uid_pmid_mapping, update_log_cg.
-
-# Usage: sh cg_update_auto.sh work_dir/
-# where work_dir specifies working directory.
-
+#!/usr/bin/env bash
 # Author: Lingtian "Lindsay" Wan
 # Monitoring : Samet Keserci
-# Date: 03/23/2016
-# Modified: 05/20/2016, Lindsay Wan, added documentation
-#           June/2016, Samet Keserci, added try/except to web request
-#           07/11/2016, Lindsay Wan, added generating check file at the end for CG generation flow.
-#           8/1/2016. Samet Keserci, revised the code for AHRQ's new website.
-#           12/09/2016, Lindsay Wan, download CG data from gateway server.
-#           12/13/2016, Lindsay Wan, move abstract extraction to front.
-#           01/09/2017, Lindsay Wan, convert html characters like &#8211 to text
-#           01/10/2017, Lindsay Wan, fixed bugs in conversion
-#           03/20/2017, Samet Keserci, revised according to migration from dev2 to dev3
+# Created: 03/23/2016
+# Modified:
+# * 05/20/2016, Lindsay Wan, added documentation
+# * June 2016, Samet Keserci, added try/except to web request
+# * 07/11/2016, Lindsay Wan, added generating check file at the end for CG generation flow.
+# * 08/01/2016. Samet Keserci, revised the code for AHRQ's new website.
+# * 12/09/2016, Lindsay Wan, download CG data from gateway server.
+# * 12/13/2016, Lindsay Wan, move abstract extraction to front.
+# * 01/09/2017, Lindsay Wan, convert html characters like &#8211 to text
+# * 01/10/2017, Lindsay Wan, fixed bugs in conversion
+# * 03/20/2017, Samet Keserci, revised according to migration from dev2 to dev3
+# * 01/08/2018, Dmitriy "DK" Korobskiy
[…]
